---
title: "Anderson"
format: dashboard
params:
  refreshdata: FALSE
  county: "Anderson"
  tableIdStart: 1
---
```{=html}
<main>
```
```{r initializing}
#| include: false
#| cache: false

refreshData <- params$refreshdata
tableId <- params$tableIdStart
if (exists("startrun")) {
  print(fortunes::fortune())
} else {
  source(here::here("Scripts","StartHere.r"))
}
if (exists("fxsVars")) {
  print(fortunes::fortune())
} else {
  source(here::here("scripts","fxsAndVars.R"))
}
source(here::here("scripts","defineColors.R"))
source(here::here("scripts","plotTheme.R"))

currentCounty <- params$county
currentMunicipalities <- paste0("municipalitiesIn",currentCounty,"NameOnly")

if (file.exists(here::here("data","clean","odsCombined.csv")) & !refreshData) {
 empData2010 <- read_csv(here::here("data","clean","odsCombined.csv")) |> 
   filter(workCountyName == currentCounty | homeCountyName == currentCounty) |>
   select(-workPlaceName,-homePlaceName) |> 
   filter(!is.na(numberOfJobs))

 } else {
   
   source(here::here("scripts", "clean.R"))
   empData2010 <- read_csv(here::here("data","clean","odsCombined.csv"))  |>
    filter(workCountyName == currentCounty  | homeCountyName == currentCounty) |>
    filter(!is.na(numberOfJobs))

 }
totalWorkJobs <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  select(numberOfJobs) |> 
  summarize(sum(numberOfJobs)) |> 
  pull()
totalHomeJobs <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  select(numberOfJobs) |> 
  summarize(sum(numberOfJobs)) |> 
  pull()

topWorkCounties <- empData2010 |> 
  filter(workCountyName == currentCounty, year == currReportYear) |> 
  group_by(homeCountyName) |>
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(homeCountyName) |> 
  pull()

topHomeCounties <- empData2010 |> 
  filter(homeCountyName == currentCounty, year == currReportYear) |> 
  group_by(workCountyName) |>
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(workCountyName) |> 
  pull()

topOverallCounties <- empData2010 |> 
  pivot_longer(cols=c(-numberOfJobs,-year),values_to = "county") |> 
  group_by(county) |> 
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(county) |> 
  pull()

topCounties <- unique(c(topWorkCounties,topHomeCounties))

empDataWorkSubset <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  mutate(
    homeCountyName=ifelse(homeCountyName %in% topHomeCounties, homeCountyName, "All Other Locations"),
    ) |> 
  group_by(homeCountyName,year) |> 
  summarize(
    numberOfJobs=sum(numberOfJobs),
    percentageOfJobs=numberOfJobs/totalWorkJobs
    ) |> 
  ungroup() |> 
  mutate(isNotOther = ifelse(homeCountyName == "All Other Locations",0,1)) |> 
  arrange(desc(isNotOther),desc(numberOfJobs) ) |> 
    select(-isNotOther)
  
empDataHomeSubset <- empData2010 |> 
  filter(homeCountyName == currentCounty) |> 
  mutate(
    workCountyName=ifelse(workCountyName %in% topWorkCounties, workCountyName, "All Other Locations"),
    ) |> 
  group_by(workCountyName,year) |> 
  summarize(
    numberOfJobs=sum(numberOfJobs),
    percentageOfJobs=numberOfJobs/totalHomeJobs
    ) |> 
  ungroup() |> 
  mutate(isNotOther = ifelse(workCountyName == "All Other Locations",0,1)) |> 
  arrange(desc(isNotOther),desc(numberOfJobs) ) |> 
    select(-isNotOther)

totalWork <- empDataWorkSubset %>% 
      summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>% 
      mutate(homeCountyName = "Total",year=NA)
  
totalHome <- empDataHomeSubset %>% 
      summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>% 
      mutate(workCountyName = "Total",year=NA)
 

if (file.exists(here::here("data","clean","acsDataCombined.csv"))) {
 acsDf <- read_csv(here::here("data","clean","acsDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County")) 
} else {
  source(here::here("scripts", "clean.R"))
  acsDf <- read_csv(here::here("data","clean","acsDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County")) 
}
if (file.exists(here::here("data","clean","ipumsPop.csv"))) {
 pumsPopDf <- read_csv(here::here("data","clean","ipumsPop.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County")) 
} else {
  source(here::here("scripts", "clean.R"))
  pumsPopDf <- read_csv(here::here("data","clean","ipumsPop.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County")) 
}

if (file.exists(here::here("data","clean","censusDataCombined.csv"))) {
 censusDf <- read_csv(here::here("data","clean","censusDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County"))
} else {
  source(here::here("scripts", "clean.R"))
  censusDf <- read_csv(here::here("data","clean","censusDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County"))
}
placesShapeFile  <- loadSfIfExists(here::here("data","clean","tigerFiles2020place.gpkg"))
countiesShapeFile <- loadSfIfExists(here::here("data","clean","tigerFiles2020county.gpkg"))


options(DT.options = list(filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    rownames=FALSE,
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    )))
# thematic::thematic_on(bg = "#222222", fg = "white", accent = "#0CE3AC", font = "Oxanium")

```


# Introduction
## Column
### Description

Topics that will be discussed in this summary report for `r currentCounty` County are

- Demographic Characteristics
  - Population growth from 1970 to 2020;
  - population density
  - sex, race, and age
  - educational level of the adult population
  - housing characteristics in terms of age of the housing stock and type of tenure
- Economic Characteristics
  - family income, household income, per capita income,
  - poverty status of families;
  - employment classification according to industry;
  - labor force by place of work and commuting patterns;

For more details on the data used, please see the [Data Description](dataDescription.qmd) tab.

### Map
```{r}
#| fig.alt: paste("A map showing the sixteen counties in ETDD with ", currentCounty, " highlighted.")

# plotly::ggplotly(
  countiesShapeFile |> 
  mutate(areaOfInterest=ifelse(NAME==currentCounty,1,0)) |> 
  filter(NAME %in% countiesInETDDNameOnly) |> 
  ggplot(aes(geometry=geom, fill=as.factor(areaOfInterest))) +
  geom_sf() +
  theme_void() +
  geom_sf_text(aes(label=NAME), size=3, color="white") +
  scale_fill_manual(values=c(etddGreenOnWhite, etddBlue)) +
  theme(legend.position = "none") +
  labs(
  alt = paste("A map showing the sixteen counties in ETDD with ", currentCounty, " highlighted.")
)
  # )

```


# Demographics {.tabset}
## Container{.tabset}
### Population and Growth 
::::{.columns}
```{r}
#| label: popTable
varsWithoutAComma <- pumsPopDf |> select(-NAME) |> names()
pumsPopDf |> 
  DT::datatable(
  colnames = c('Place' = 'NAME'),
  caption=str_c("source: ",nhgisCitation),
  elementId = paste0("DataTables_",tableId),   rownames = FALSE,
  extensions = c('Buttons', 
     'FixedHeader'),
  options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download'
      ))
  )) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency(varsWithoutAComma, currency = "", digits=1)
tableId <- tableId+1
```
::: {.card}
```{r} 
#| label: popGraph
#| fig.alt: "A line graph showing the population data"
# renderings: [light, dark]
# plotly::plotlyOutput(outputId = paste0("plot_",tableId))
# plotly::renderPlotly(
p <- pumsPopDf |> 
  pivot_longer(
    cols = c(-NAME,-starts_with("Change")),
    names_to = "year",
    values_to = "population"
  ) |> 
  mutate(year=factor(year)) |> 
  select(-starts_with("Change")) |> 
  filter(!is.na(population)) |> 
  mutate(text = paste(
    "<b>", NAME, "</b>",
    "<br><b>Year: </b>", year,
    "<br><b>Population: </b> ", prettyNum(population,big.mark = ","),
    sep="")) |> 
  ggplot( aes(x = year,
                     y = population, 
                     color = NAME,
              text = text,
              group=NAME)) +
  geom_line()+
  geom_point()+
  labs(
    caption = nhgisCitation,
    color="Place",
    y="Population",
    x=("Year")
    # x=str_c("Year<br>","source: ",nhgisCitation)
  ) +
  scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )

# thematic::thematic_set_theme(theme_light)
plotly::ggplotly(p, tooltip="text")
# thematic::thematic_set_theme(theme_dark)
# plotly::ggplotly(p)
```

`{r} nhgisCitation`
:::
:::::
### Population Density 

:::: {.columns}


```{r}
#| label: popDensityTable
censusDf |> filter(cleanedLabel=="area" | cleanedLabel == "populationDensity") |> 
  pivot_wider(values_from = value, names_from = cleanedLabel) |> 
  mutate(NAME=ifelse(NAME=="Rocky Top","Rocky Top(a)",NAME)) |> 
  select(-GEOID,-concept, -year) |> 
  DT::datatable(
    caption = str_c("Density is population / area (in square miles); <br>source: ",Census_2010Cite," and ",Census_2020Cite),
  colnames = c('Place' = 'NAME', 'Population Density' = 'populationDensity','Area'='area'),
    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Area', currency = "", digits=1) |> 
  DT::formatCurrency('Population Density', currency = "", digits=1)
tableId <- tableId+1
```
::: {.card}

```{r}
#| label: popDensityFig
#| fig.alt: "A bar graph showing the population density data"

# longestLabel=censusDf |> select(NAME) |> distinct() |> mutate(len=str_length(NAME)) |> 
#   slice_max(order_by = len,n=1) |> select(len) |> pull()
# longestAxis=longestLabel*12*0.6*sin(45)

(
plotly::ggplotly((censusDf |> filter(cleanedLabel == "populationDensity") |> 
                    mutate(text = paste(
                    "<b>", NAME, "</b>",
                    "<br><b>Population Density: </b>", prettyNum(value,digits=1,big.mark = ","),
                    sep="")) |> 
  ggplot(aes(x=NAME,y=value, text=text)) +
  geom_bar(stat='identity', fill=barColor,color=barOutlineColor)+
  labs(y="Population Density",
       # x=str_c("Density is population / area (in square miles)<br>source: ",Census_2020Cite))+
              x=str_c("Density is population / area (in square miles)"))+

  # annotate("text",x = 1, y = -1, hjust=100, vjust=-50,
           # label="Density is population / area (in square miles); source: @Census_2020")+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )), tooltip="text"
  )
) 
  # plotly::add_annotations(text = "Density is population / area (in square miles); source: @Census_2020.")
  


```
source: @Census_2020
:::
::::


### Population Descriptions
:::: {.columns}
:::{.row}
```{r}
#| label: popDescRaceTable

pctVarName <- "Percentage of People"
max_num <- acsDf |> 
  filter(concept=="AGE AND SEX") |> 
  filter(str_detect(cleanedLabel,"Total population"), !str_detect(cleanedLabel,"TotalTotal")) |> 
  select(estimate) |> 
  slice_max(
    order_by = estimate,
    n = 1
  ) |>
  pull(estimate)

popPyramidData <- acsDf |> filter(concept=="AGE AND SEX") |> filter(str_detect(cleanedLabel,"Total population")) |> 
  mutate(Sex = ifelse(str_detect(cleanedLabel,"Female"),"Female",
                      ifelse(str_detect(cleanedLabel,"Male"),"Male",NA)),
         AgeRange = str_remove(str_remove(str_remove(cleanedLabel, 
                                                     "FemaleTotal populationAGE"),
                                          "MaleTotal populationAGE"),
                               "TotalTotal populationAGE"),
         estimate=ifelse(Sex == "Female", -estimate, estimate),
         AgeRange=factor(AgeRange, levels=c("Under 5 years",
                                               "5 to 9 years",
                                               "10 to 14 years", 
                                                "15 to 19 years",   
                                                "20 to 24 years",   
                                                "25 to 29 years",   
                                                "30 to 34 years",   
                                                "35 to 39 years",   
                                                "40 to 44 years",   
                                                "45 to 49 years",   
                                                "50 to 54 years",   
                                                "55 to 59 years",   
                                                "60 to 64 years",   
                                                "65 to 69 years",   
                                                "70 to 74 years",   
                                                "75 to 79 years",   
                                                "80 to 84 years",   
                                                "85 years and over"
                                               ))
         ) |> 
  rbind(
    acsDf |> 
      filter(concept=="AGE AND SEX") |> 
      filter(str_detect(cleanedLabel,"Total population"),str_detect(cleanedLabel,"TotalTotal")) |> 
      group_by(NAME,concept,year) |> summarize(estimate=sum(estimate)) |>   
      mutate(cleanedLabel="Total",AgeRange=NA,Sex=NA)
  ) |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2020, valueVarName="estimate") |> 
  mutate(`Percentage of People` = abs(`Percentage of People`)) |> 
    filter(!is.na(AgeRange), !is.na(Sex)) 


censusDf |> 
  filter(concept=="RACE", !is.na(cleanedLabel)) |>
  addPercentVar(pctVarName, totalVarValue="Total", year=2020, valueVarName="value") |> 
  filter( cleanedLabel != "Total") |> 
  select(NAME, year, cleanedLabel, value, any_of(pctVarName)) |> 
DT::datatable(
  colnames = c('Place' = 'NAME','Number of People' = 'value',
               'Race Category' = 'cleanedLabel', 'Year' = 'year'),
  caption = str_c("source: ",Census_2010Cite," and ", Census_2020Cite),
    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )
  ) |> 
  DT::formatCurrency('Number of People', currency = "", digits=0) |> 
  DT::formatPercentage(pctVarName, digits=2)
tableId <- tableId+1
```
``` {r}
#| label: popAgeTable
 
popPyramidData |> 
  # pivot_wider(values_from = value, names_from = cleanedLabel) |> 
  select(NAME, Sex, AgeRange, year, estimate, any_of(pctVarName)) |> 
  mutate(estimate=abs(estimate)) |> 
  DT::datatable(
  colnames = c('Place' = 'NAME', 'Age Range' = 'AgeRange','Year'='year', 
               'Number of People' = 'estimate'),
  caption = str_c("source: ",Census_2010Cite," and ",Census_2020Cite),
    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Number of People', currency = "", digits=0) |> 
  DT::formatPercentage(pctVarName, digits=2)
# Sex
  tableId <- tableId+1
```
::::

::::{.row}
:::{.card}
```{r}
#| label: popRaceGraph
#| fig.alt: "A bar graph showing the racial category data"

p <-  (censusDf |> filter(concept=="RACE", cleanedLabel != "Total", !is.na(cleanedLabel)) |> 
                    mutate(text = paste(
                    "<b>", NAME, "</b>",
                    "<br><b>Racial Category: </b>", cleanedLabel,
                    "<br><b>Estimated Population: </b>", prettyNum(value,big.mark = ","),
                    sep="")) |>
  ggplot(aes(x=cleanedLabel, y=value, fill=NAME, text=text))+
  geom_bar(stat="identity",position="dodge",color=barOutlineColor)+
  labs(
    # x=str_c("Racial Category<br>source: ",Census_2020Cite),
    x=str_c("Racial Category"),
    y="Estimated Population",
    fill="Place"
  ) +
  scale_y_continuous(
    labels = scales::comma,
    breaks = breaks_pretty()
  ))
plotly::ggplotly(p, tooltip = "text")

```
source: @Census_2020
:::
:::{.card}

``` {r}
#| label: popPyramid
#| fig.alt: "A bar graph showing the population age and sex data"

population_pyramid_men <- popPyramidData |>
  filter(Sex == "Male", NAME==str_c(currentCounty, " County")) |>
  ggplot(aes(
    x = estimate,
    y = AgeRange
    
  )) +
  geom_col(fill=etddBlueDark)+
  annotate(
    geom = "label",
    x = 2*(max_num/3),
    y = 17,
    label = "Male",
    fill = etddBlueDark,
    color = "white",
    label.padding = unit(0.3, "lines")
  ) +
  scale_x_continuous(
    labels = scales::comma,
    breaks = breaks_pretty(),
    limits = c(0, max_num)
  ) +
  labs(x="",y="", caption=str_c("data for ", currentCounty))+
  theme(
    axis.title.y=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.x = element_text(),
    axis.line.y= element_blank(),
    panel.grid.major.x = element_line(color = "grey90")
  )
population_pyramid_women <-
  popPyramidData |>
  filter(Sex == "Female", NAME==str_c(currentCounty, " County")) |>
  ggplot(aes(
    x = estimate,
    y = AgeRange
   
  )) +
  geom_col(fill = etddGreen) +
  annotate(
    geom = "label",
    x =  -(2*(max_num/3)),
    y = 17,
    label = "Female",
    fill = etddGreenOnWhite,
    color = "white",
    
    label.padding = unit(0.3, "lines")
  ) +
  scale_x_continuous(
    labels = function(x) scales::comma(abs(x)),
    breaks = breaks_pretty(),
    limits = c(-max_num, 0)
  ) +
  labs(x="",y="")+
  theme(
    axis.title.y=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.x = element_text(),
    axis.line.y= element_blank(),
    panel.grid.major.x = element_line(color = "grey90")
  )

  age_labels_plot <-
  popPyramidData |> 
    select(AgeRange) |> distinct() |> 
  ggplot(
    aes(
      x = 1,
      y = AgeRange,
      label = AgeRange
    )
  ) +
  geom_text() +
  theme_void()
  

  population_pyramid_women +
  age_labels_plot +
  population_pyramid_men +
  plot_layout(
    widths = c(7.5, 3.5, 7.5)
  )



```
source: @ACS_2020
:::
::::
:::::
### Education
::::{.columns}
```{r}
#| label: eduTable

acsDf |> 
  filter(concept == "SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER"  &
           cleanedLabel != "Other") |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2020) |>
  addPercentVar(pctVarName, totalVarValue="Total", year=2010) |>
  select(-concept) |> 
  DT::datatable(
  colnames = c('Place' = 'NAME', 'Level of Education' = 'cleanedLabel', 'Number of People' = 'estimate', 'Year'='year'),
  caption = str_c("source: ",ACS_2010Cite," and ", ACS_2020Cite),
    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )
  ) |> 
  DT::formatPercentage(pctVarName, 0) |>
  DT::formatCurrency('Number of People', currency = "", digits=0)
tableId <- tableId+1
```

::: {.card}

```{r}
#| label: eduGraph
#| fig.alt: "A bar graph showing the education level data"

p <- acsDf |> 
     filter(concept == "SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER", cleanedLabel!="Other",cleanedLabel!="Total", year==currReportYear) |> 
  mutate(cleanedLabel = factor(cleanedLabel, levels=c(
    "Less Than 9th Grade",
    "9th to 12th Grade, No Diploma",
    "Some College, No Degree",
    "Associate's degree",
    "Bachelor's degree",
    "Graduate or Professional Degree"
  ))) |> 
  mutate(text = paste(
                    "<b>", NAME, "</b>",
                    "<br><b>Education Category: </b>", cleanedLabel,
                    "<br><b>Estimated Population: </b>", prettyNum(estimate,big.mark = ","),
                    sep="")
         ) |> 
     ggplot(aes(x=cleanedLabel, y=estimate, fill=NAME, text=text)) +
     geom_bar(stat="identity", position="dodge",color=barOutlineColor)+
  labs(x=str_c("Education Category"),,y="Estimated Population", fill="Place")+
  scale_y_continuous(
    labels = scales::comma,
    breaks = breaks_pretty()
  )
  
plotly::ggplotly(p, tooltip="text")

```
source: @ACS_2020
:::
:::::
### Housing Units by Year of Construction
::::{.columns}
```{r}
#| label: constYearTable
tmpDf <- acsDf |> filter(concept == "YEAR STRUCTURE BUILT") |> 
  pivot_wider(
    names_from = cleanedLabel,
    values_from = estimate
  ) |> 
  select(-concept)
varsWithAComma <- tmpDf |>  select(-NAME,-year) |> names()

tmpDf |> 
    relocate(Total, .after = last_col()) |> 
  DT::datatable(
    caption = str_c("Housing Units by Year of Construction, <br>source: ",Census_2010Cite," and ",Census_2020Cite),
  colnames = c('Place' = 'NAME', 'Year'='year'),
    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  DT::formatCurrency(varsWithAComma, currency = "", digits=0)
tableId <- tableId+1
```
:::{.card}
```{r}
#| label: constYearGraph
#| fig.alt: "A bar graph showing the construction year data"
plotly::ggplotly(
acsDf |> 
 filter(concept == "YEAR STRUCTURE BUILT" & cleanedLabel != "Total", cleanedLabel !="EstimateTotal",, year==currReportYear) |> 
  mutate(cleanedLabel=str_remove(cleanedLabel,"EstimateTotalBuilt ")) |> 
  group_by(NAME) |> 
  mutate(totalForPlace=sum(estimate)) |> 
  ungroup() |> 
  mutate(text = paste(
                    "<b>", NAME, "</b>",
                    "<br><b>Year Structure Built: </b>", cleanedLabel,
                    "<br><b>Percent: </b>", round((estimate/totalForPlace)*100,0), "%",
                    sep="")
         ) |> 
ggplot(aes(x = NAME,
           fill = cleanedLabel, y = estimate, text=text)) + 
  geom_bar(position = "fill", stat = "identity",color=barOutlineColor) +
  labs(y = "Percent", 
       fill="Year Structure Built",
       # x=str_c("source: ",Census_2020Cite),
       x="",
       title = "Year Structure Built by Place")+
   # scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::percent,
     breaks=pretty_breaks()
   ), tooltip="text"
)
```
source: @Census_2020
:::
:::::
### Housing Units by Type of Tenure
::::{.columns}
```{r}
#| label: tenureTypeTable

tmpDf <- acsDf |> filter(concept == "TENURE") |> 
  pivot_wider(
    names_from = cleanedLabel,
    values_from = estimate
  ) |> 
  select(-concept)
varsWithAComma <- tmpDf |>  select(-NAME,-year) |> names()

tmpDf |> 
  DT::datatable(
    
  caption = str_c("Housing Units by Tenure Status; \nsource: ",ACS_2020Cite," and ",ACS_2010Cite),
  colnames = c('Place' = 'NAME','Year'='year'),
    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  DT::formatCurrency(varsWithAComma, currency = "", digits=0)
tableId <- tableId+1
```
:::{.card}
```{r}
#| label: tenureTypeGraph
#| fig.alt: "A bar graph showing the tenure type data"
plotly::ggplotly(acsDf |> filter(concept == "TENURE", year==currReportYear, cleanedLabel != "Total") |> 
                   mutate(text = paste(
                    "<b>", NAME, "</b>",
                    "<br><b>Type of Tenure: </b>", cleanedLabel,
                    "<br><b>Estimated Number of Houses: </b>", prettyNum(estimate,big.mark = ","),
                    sep="")
         ) |> 
  ggplot(aes(x=NAME, y= estimate, fill = cleanedLabel, text=text)) +
    geom_bar(position = position_dodge(preserve = "single"),stat="identity",color=barOutlineColor)+
  labs(y="Estimated Number of Houses",
       # x=str_c("source: ",Census_2020Cite),
       x="",
       fill="Type of Tenure")+
  # scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   ), tooltip="text")
```
source: @Census_2020
:::
:::::

# Economics
## Container{.tabset}
#### Income Comparison
::::{.columns}
```{r}
#| label: incomeTable
varsWithAComma <- acsDf |> 
  filter(concept == "PER CAPITA INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)" | concept == "INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)", cleanedLabel != "Other") |> 
   select(-concept) |> 
  pivot_wider(values_from = estimate,names_from = cleanedLabel) |> select(-NAME,-year) |> names()

acsDf |> 
  filter(concept == "PER CAPITA INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)" | concept == "INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)", cleanedLabel != "Other") |> 
   select(-concept) |> 
  pivot_wider(values_from = estimate,names_from = cleanedLabel)|> 
  DT::datatable(
  colnames = c('Place' = 'NAME', 'Year'='year'),
    caption = str_c("source: ",ACS_2010Cite," and ",ACS_2020Cite),
    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency(varsWithAComma, currency = "$", digits=0)
tableId <- tableId+1
```
:::{.card}
``` {r}
#| label: incomeGraph
#| fig.alt: "A bar graph showing the per capita income"
plotly::ggplotly(
acsDf |> 
  filter(concept == "PER CAPITA INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)", year==currReportYear) |> 
  mutate(text = paste(
                    "<b>", NAME, "</b>",
                    "<br><b>Income (per capita):</b> $", prettyNum(estimate,big.mark = ","),
                    sep="")
         ) |> 
  ggplot(aes(x=estimate, y=reorder(NAME, estimate),text=text)) +
  geom_segment(aes(x = 40, 
               xend = estimate, 
               y = reorder(NAME, estimate), 
               yend = reorder(NAME, estimate)),
               color = barOutlineColor) +
  geom_point(color=barColor, size = 2) +
  labs(x="Income (per capita)",
  # labs (x=str_c("Income (per capita)<br><span style=\'font-size: ",citeFontSize,";\'>source: ","U. S. Census Bureau Decennial Census: Redistricting Data (PL 94-171), 2020, <br>accessed June 2, 2026, http://api.census.gov/data/2020/dec/pl.","</span>"),
        y = "",
        title = "Income by Municipality",
        subtitle = str_c("(",currentCounty," County)")) +
  theme_minimal() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
   scale_x_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   ), tooltip="text")
```
source: @Census_2020
:::
:::::

#### Povery Status
::::{.columns}
```{r}
#| label: povertyTable
acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel == "Above Poverty" | cleanedLabel == "Below Poverty") |> 
  select(NAME,cleanedLabel,year,estimate) |> 
  pivot_wider(names_from = cleanedLabel,values_from = estimate) |> 
DT::datatable(
    colnames = c('Place' = 'NAME', 'Year'='year'),
      caption = str_c("source: ",ACS_2010Cite," and ",ACS_2020Cite),

      elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Above Poverty', currency = "", digits=0) |> 
  DT::formatCurrency('Below Poverty', currency = "", digits=0)
tableId <- tableId+1
```
:::{.card}
```{r}
#| label: povertyGraph
#| fig.alt: "A bar graph showing poverty status data"
plotly::ggplotly(acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel == "Above Poverty" | cleanedLabel == "Below Poverty") |> 
                   mutate(text = paste(
                    "<b>", NAME, "</b>",
                    "<br><b>Povery Status: </b>", cleanedLabel,
                    "<br><b>Estimated Number of Families: </b>", prettyNum(estimate,big.mark = ","),
                    sep="")
         ) |> 
  ggplot(aes(x=NAME, y=estimate, fill=cleanedLabel, text=text))+
  geom_bar(stat = "identity", position = "dodge",color=barOutlineColor)+
  labs(y="Estimated Number of Families",
       x="",
       # x=str_c("source: ",Census_2020Cite),
       fill="Poverty Status")+
  # scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   ), tooltip="text"
)
```
source: @ACS_2020
:::
:::::

#### Poverty Status by Family Type
::::{.columns}
```{r}
#| label: povertyFamilyTable
pctVarName = "Percentage of Families"

acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel != "Other", cleanedLabel != "Total") |> 
  select(NAME,cleanedLabel,year,estimate) |> 
  mutate(`Poverty Status` = ifelse(str_detect(cleanedLabel,"Above Poverty"),"Above Poverty","Below Poverty"),
         `Family Type` = case_when(
           str_detect(cleanedLabel, "Female Householder with related children")
           ~ "Female Householder with related children",
           str_detect(cleanedLabel,"Female Householder")
           ~ "Female Householder",
           .default="All Families"
         )
  ) |> 
  select(-cleanedLabel) |>
  relocate(estimate, .after = last_col()) |> 
  relocate(year, .after = last_col()) |> 
    addPercentVar(pctVarName, totalVarValue="All Families", totalVarName = "Family Type", year=2020) |>
  addPercentVar(pctVarName, totalVarValue="All Families", totalVarName = "Family Type", year=2010) |>
  # pivot_wider(names_from = cleanedLabel,values_from = estimate) |> 
DT::datatable(
  colnames = c('Place' = 'NAME', 'Year'='year', 'Number of Families'='estimate'),
    caption = str_c("source: ",ACS_2010Cite, " and ",ACS_2020Cite),

    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  # DT::formatCurrency('Above Poverty', currency = "", digits=0) |> 
  DT::formatCurrency('Number of Families', currency = "", digits=0) |> 
  DT::formatPercentage(pctVarName, digits=2)
tableId <- tableId+1
```
::::{.row}
:::{.card}
```{r}
#| label: povertyFamilyGraph
#| fig.alt: "A bar graph showing the poverty status by family data"
plotly::ggplotly(
acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel != "Other", cleanedLabel != "Total", year==2020, NAME=="Anderson County") |> 
  select(NAME,cleanedLabel,year,estimate) |> 
   mutate(`Poverty Status` = ifelse(str_detect(cleanedLabel,"Above Poverty"),"Above Poverty","Below Poverty"),
         `Family Type` = case_when(
           str_detect(cleanedLabel, "Female Householder with related children")
           ~ "Female Householder with related children",
           str_detect(cleanedLabel,"Female Householder")
           ~ "Female Householder",
           .default="All Other Families"
         )
  ) |> 
  summarize(estimate=sum(estimate), .by = c(`Poverty Status`,`Family Type`))|> 
  mutate(text = paste(
                    "<b>", currentCounty, "</b>",
                    "<br><b>Poverty Status: </b>", `Poverty Status`,
                    "<br><b>Family Type: </b>", `Family Type`,
                    "<br><b>Estimated Number of Families: </b>", prettyNum(estimate,big.mark = ","),
                    sep="")
         ) |> 
  mutate(`Family Type` = ifelse(`Family Type` == "Female Householder with related children",
                                "Female Householder with<br>related children",`Family Type`)) |> 
  ggplot(aes(x=`Poverty Status`,y=estimate,fill=`Family Type`, text=text))+
  geom_bar(stat="identity", position="stack", color=barOutlineColor)+
  labs(y="Estimated Number of Families",
       # x=str_c("source: ",Census_2020Cite),
       fill="Family Type")+
  # scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   ), tooltip = "text")
```
source: @ACS_2020
:::
::::
:::::

#### Employment by Industry
::::{.columns}
```{r}
#| label: empTable

topIndustries <- acsDf |> filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other" & cleanedLabel != "EstimateTotal" & cleanedLabel != "Total", year==currReportYear) |> 
  mutate(cleanedLabel = str_remove(cleanedLabel,"([\\w\\s\\,&]*:\\s?)")) |> 
  select(-concept) |> 
  group_by(cleanedLabel) |>
  summarize(numberOfJobs=sum(estimate)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopIndustries) |> 
  select(cleanedLabel) |> 
  pull()

pctVarName <- "Percentage of Jobs"

acsDf |> 
filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other") |> 
  mutate(cleanedLabel = str_remove(cleanedLabel,"([\\w\\s\\,&]*:\\s?)"),
         cleanedLabel = ifelse(cleanedLabel %in% topIndustries | cleanedLabel == "Total", cleanedLabel, "Other Industries")) |> 
  group_by(NAME,cleanedLabel,year) |> 
  summarize(estimate=sum(estimate)) |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2020) |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2010) |> 
  filter(cleanedLabel != "EstimateTotal" & cleanedLabel != "Total") |> 
DT::datatable(
  colnames = c('Place' = 'NAME', 'Year'='year', 'Number of Jobs' = 'estimate', 'Industry'='cleanedLabel'),
    caption = str_c("source: ",ACS_2010Cite," and ",ACS_2020Cite),

    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  DT::formatCurrency('Number of Jobs', currency='', digits=0) |> 
  DT::formatPercentage(pctVarName,digits=2)
tableId <- tableId+1
```
:::{.card}
```{r}
#| label: empGraph
#| fig.alt: "A bar graph showing employment by industry"
plotly::ggplotly(
acsDf |> filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other" & cleanedLabel != "EstimateTotal" & cleanedLabel != "Total",year==currReportYear) |> 
  mutate(cleanedLabel = str_remove(cleanedLabel,"([\\w\\s\\,&]*:\\s?)"),
         cleanedLabel = ifelse(cleanedLabel %in% topIndustries, cleanedLabel, "Other Industries")) |> 
  group_by(NAME,cleanedLabel,year) |> 
  summarize(estimate=sum(estimate)) |> 
  mutate(text = paste(
                    "<b>", NAME, "</b>",
                    "<br><b>Industry Category: </b>", cleanedLabel,
                    "<br><b>Estimated Number of Workers: </b>", prettyNum(estimate,big.mark = ","),
                    sep="")
         ) |> 
  ggplot(aes(y=estimate, x=NAME, fill = cleanedLabel, text=text))+
  geom_bar(stat = "identity", position = "dodge",color=barOutlineColor)+
  theme(legend.position = "none")+
  labs(y="Estimated Number of Workers",
       # x=str_c("source: ",Census_2020Cite),
       x="",
       fill="Industry Category")+
  # scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   ), tooltip= "text"
)

```
source: @ACS_2020
:::
:::::

#### Employment by Industry (Historical)
::::{.columns}
```{r}
#| label: empHistTable

acsDf |> filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other" ) |> 
  mutate(cleanedLabel = str_remove(cleanedLabel,"(:[\\w\\s,&]*)")) |> 
  select(-concept) |> 
  group_by(NAME,year,cleanedLabel) |> 
  summarize(estimate=sum(estimate)) |> 
  ungroup() |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2020) |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2010) |> 
  filter(cleanedLabel != "EstimateTotal" & cleanedLabel != "Total") |> 
DT::datatable(
  colnames = c('Place' = 'NAME', 'Year'='year', 'Number of Jobs' = 'estimate', 'Industry'='cleanedLabel'),
    caption = str_c("source: ",ACS_2010Cite," and ",ACS_2020Cite),

    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  DT::formatCurrency('Number of Jobs', currency='', digits=0) |> 
  DT::formatPercentage(pctVarName, digits=2)
tableId <- tableId+1
```
:::::
#### Labor Force by Place of Work
::::{.columns}
```{r}
#| label: placeWorkTable

acsDf |> 
  filter(concept=="MEANS OF TRANSPORTATION TO WORK BY PLACE OF WORK--STATE AND COUNTY LEVEL", cleanedLabel!="Other", cleanedLabel !="Total") |>
  select(-concept) |> 
  pivot_wider(values_from = estimate,names_from = cleanedLabel) |> 
  
DT::datatable(
    colnames = c('Place' = 'NAME', 'Year'='year'),
      caption =str_c("source: ",ACS_2010Cite," and ", ACS_2020Cite),

      elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  DT::formatCurrency('Work Out Of State', currency='', digits=0) |> 
  DT::formatCurrency('Work Out of County of Residence', currency='', digits=0) |> 
  DT::formatCurrency('Work in County of Residence', currency='', digits=0) 
tableId <- tableId+1
```
:::{.card}
```{r}
#| label: placeWorkGraph
#| fig.alt: "A bar graph showing the percentage of people who work in the county, out of the county, or in another state"

plotly::ggplotly(
acsDf |> filter(concept=="MEANS OF TRANSPORTATION TO WORK BY PLACE OF WORK--STATE AND COUNTY LEVEL", cleanedLabel!="Other",cleanedLabel !="Total") |> 
  mutate(text = paste(
                    "<b>", NAME, "</b>",
                    "<br><b>Place of Work:</b>",cleanedLabel,
                    "<br><b>Estimated Number of Jobs: </b>", prettyNum(estimate,big.mark = ","),
                    sep="")
         ) |> 
  ggplot(aes(x=cleanedLabel,y=estimate,fill=NAME, text=text))+
  geom_bar(stat="identity",color=barOutlineColor, position="dodge",color=barOutlineColor)+
  labs(y="Estimated Number of Workers",
       # x=str_c("source: ",Census_2020Cite),
       x="",
       fill="Place of Residence")+
  # scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   ), tooltip = "text"
)
```
source: @ACS_2020
:::
:::::
#### Commuting Patterns
::::{.columns}
```{r}
#| label: commutingTables
#| 

pctVars <- c("percentageOfJobs")
pctWholeVars <- c("")

empDataWorkSubset |> 
  bind_rows(totalWork) |> 
 DT::datatable(
  caption = str_c(currentCounty," Laborers Residing in Anderson County by County Where They Work, <br>source: ",lodesCite),
  colnames = c('Home County' = 'homeCountyName', 'Number of Jobs' = 'numberOfJobs', 'Percentage of Jobs' = 'percentageOfJobs', 'Year'='year'),
    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  DT::formatPercentage('Percentage of Jobs', 0) |> 
  DT::formatCurrency('Number of Jobs', currency = "", digits=0)
empDataHomeSubset |> 
  bind_rows(totalHome) |> 
 DT::datatable(
  caption = str_c(currentCounty," Laborers Working in Anderson County by County Where They Reside, <br>source: ",lodesCite),
  colnames = c('Work County' = 'workCountyName', 'Number of Jobs' = 'numberOfJobs', 'Percentage of Jobs' = 'percentageOfJobs','Year'='year'),
    elementId = paste0("DataTables_",tableId),   rownames = FALSE,   extensions = c('Buttons',       'FixedHeader'),   options = list(     dom = 'Bfrtip',     buttons =        list('copy', 'print', list(         extend = 'collection',         buttons = c('csv', 'excel', 'pdf'),         text = 'Download'       ))   )

  ) |> 
  DT::formatPercentage('Percentage of Jobs', 0) |> 
  DT::formatCurrency('Number of Jobs', currency = "", digits=0)
tableId <- tableId+1
```
:::{.card}
``` {r}
#| label: commutingGraphs
#| fig.alt: "A bar graph showing where people commute to and from"

plotly::ggplotly(
(empDataWorkSubset |> 
    filter(year==currReportYear) |> 
   mutate(text = paste(
                    "<b>", homeCountyName, "</b>",
                    "<br><b>Estimated Number of Jobs: </b>", prettyNum(numberOfJobs,big.mark = ","),
                    sep="")
         ) |> 
  ggplot(aes(x=homeCountyName,y=numberOfJobs, text=text)) +
  geom_bar(stat = "identity",fill=barColor,color=barOutlineColor)+
  # labs(x=str_c("Home County<br>source: ",Census_2020Cite),
     labs(x=str_c("Home County"),

       y = "Number of Jobs", 
       title = "Laborers Working in Anderson County",
       subtitle="Commuting Patterns")+
     scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )) , tooltip="text"
  )

plotly::ggplotly(
(empDataHomeSubset |> 
    filter(year==currReportYear) |> 
      mutate(text = paste(
                    "<b>", workCountyName, "</b>",
                    "<br><b>Estimated Number of Jobs: </b>", prettyNum(numberOfJobs,big.mark = ","),
                    sep="")
         ) |> 
  ggplot(aes(x=workCountyName,y=numberOfJobs, text=text)) +
  geom_bar(stat = "identity",fill=barColor,color=barOutlineColor)+
  # labs(x=str_c("Work County<br>source: ",Census_2020Cite),
     labs(x=str_c("Work County"),
       y = "Number of Jobs", 
       title = "Laborers Residing in Anderson County",
       subtitle="Commuting Patterns")+
     scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )) , tooltip = "text"
  )
```
source: @lodes
:::
:::::
```{=html}
</main>
```
