---
title: | 
  ![](../resources/ETDDLogo.svg){width=1in} ETDD Census Data
logo:
    small: ../resources/ETDDLogo.svg
    medium: ../resources/ETDDLogo.svg
format: 
  dashboard: 
      css: ../resources/oddHighlight.css
      theme: 
        light: flatly
        dark: darkly
      scrolling: true
embed-resources: true
execute: 
  cache: true
params:
  refreshdata: FALSE
---

```{r initializing}
#| include: false
#| cache: true

if (exists("startrun")) {
  print(fortunes::fortune())
} else {
  source(here::here("Scripts","StartHere.r"))
}
if (exists("fxsVars")) {
  print(fortunes::fortune())
} else {
  source(here::here("scripts","fxsAndVars.R"))
}
source(here::here("scripts","defineColors.R"))

currentCounty <- "Anderson"
currentMunicipalities <- municipalitiesInAnderson

}

if (file.exists(here::here("data","clean","odsCombined.csv")) & !refreshData) {
 empData2010 <- read_csv(here::here("data","clean","odsCombined.csv")) |> 
   filter(workCountyName == currentCounty | homeCountyName == currentCounty) |>
   select(-workPlaceName,-homePlaceName) |> 
   filter(!is.na(numberOfJobs))

 } else {
   
   source(here::here("scripts", "clean.R"))
   empData2010 <- read_csv(here::here("data","clean","odsCombined.csv"))  |>
    filter(workCountyName == currentCounty  | homeCountyName == currentCounty) |>
    filter(!is.na(numberOfJobs))

 }
totalWorkJobs <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  select(numberOfJobs) |> 
  summarize(sum(numberOfJobs)) |> 
  pull()
totalHomeJobs <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  select(numberOfJobs) |> 
  summarize(sum(numberOfJobs)) |> 
  pull()

topWorkCounties <- empData2010 |> 
  filter(workCountyName == currentCounty, year == currReportYear) |> 
  group_by(homeCountyName) |>
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(homeCountyName) |> 
  pull()

topHomeCounties <- empData2010 |> 
  filter(homeCountyName == currentCounty, year == currReportYear) |> 
  group_by(workCountyName) |>
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(workCountyName) |> 
  pull()

topOverallCounties <- empData2010 |> 
  pivot_longer(cols=c(-numberOfJobs,-year),values_to = "county") |> 
  group_by(county) |> 
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(county) |> 
  pull()

topCounties <- unique(c(topWorkCounties,topHomeCounties))

empDataWorkSubset <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  mutate(
    homeCountyName=ifelse(homeCountyName %in% topHomeCounties, homeCountyName, "All Other Locations"),
    ) |> 
  group_by(homeCountyName,year) |> 
  summarize(
    numberOfJobs=sum(numberOfJobs),
    percentageOfJobs=numberOfJobs/totalWorkJobs
    ) |> 
  ungroup() |> 
  mutate(isNotOther = ifelse(homeCountyName == "All Other Locations",0,1)) |> 
  arrange(desc(isNotOther),desc(numberOfJobs) ) |> 
    select(-isNotOther)
  
empDataHomeSubset <- empData2010 |> 
  filter(homeCountyName == currentCounty) |> 
  mutate(
    workCountyName=ifelse(workCountyName %in% topWorkCounties, workCountyName, "All Other Locations"),
    ) |> 
  group_by(workCountyName,year) |> 
  summarize(
    numberOfJobs=sum(numberOfJobs),
    percentageOfJobs=numberOfJobs/totalHomeJobs
    ) |> 
  ungroup() |> 
  mutate(isNotOther = ifelse(workCountyName == "All Other Locations",0,1)) |> 
  arrange(desc(isNotOther),desc(numberOfJobs) ) |> 
    select(-isNotOther)

totalWork <- empDataWorkSubset %>% 
      summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>% 
      mutate(homeCountyName = "Total",year=NA)
  
totalHome <- empDataHomeSubset %>% 
      summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>% 
      mutate(workCountyName = "Total",year=NA)
 

if (file.exists(here::here("data","clean","acsDataCombined.csv"))) {
 acsDf <- read_csv(here::here("data","clean","acsDataCombined.csv")) |> filter(NAME %in% currentMunicipalities | NAME == str_c(currentCounty," County")) 
} else {
  source(here::here("scripts", "clean.R"))
  acsDf <- read_csv(here::here("data","clean","acsDataCombined.csv")) |> filter(NAME %in% currentMunicipalities | NAME == str_c(currentCounty," County")) 
}
if (file.exists(here::here("data","clean","censusDataCombined.csv"))) {
 censusDf <- read_csv(here::here("data","clean","censusDataCombined.csv")) |> filter(NAME %in% currentMunicipalities | NAME == str_c(currentCounty," County"))
} else {
  source(here::here("scripts", "clean.R"))
  censusDf <- read_csv(here::here("data","clean","censusDataCombined.csv")) |> filter(NAME %in% currentMunicipalities | NAME == str_c(currentCounty," County"))
}


```

# Overview

## Row {.tabset}

### Overview of this product

### Description of the data and data sources

### Shiny App (to add later)

# Anderson

## Row {.tabset}
### Description

PUT MAP HERE

INTRODUCTION
This report is part of a series, which examines statistical data from U.S. Census materials regarding
economic and demographic characteristics in the sixteen counties that make up the East
Tennessee Development District. The series utilizes data from U.S. Decennial Censuses along with
American Community Survey Five-year Estimates as its primary sources. Please see the Data Description Tab for a detailed list of where the data comes from.

Topics that will be discussed in this summary report for Anderson County are
• population growth from 1950 to 2020;
• population density;
• demographic characteristics in terms of sex, race, and age;
• economic characteristics in terms of family income, household income, per capita income,
and poverty status of families;
• employment classification according to industry;
• labor force characteristics in terms of place of work and commuting patterns;
• educational level of the adult population;
• and housing characteristics in terms of age of the housing stock and type of tenure.

### Demographics{.tabset}

```{r}
#| title: Population and Growth

censusDf |> filter(concept == "RACE", cleanedLabel=="Total")

```


```{r}
#| title: Population Density



```


```{r}
#| title: Population Descriptions

# totalOfRace <- censusDf |> (concept == "RACE" & cleanedLabel == "Total") |> pull()
# totalOfSex <- censusDf |> (concept == "RACE" & cleanedLabel == "Total") |> pull()
# totalOfAge <- censusDf |> (concept == "RACE" & cleanedLabel == "Total") |> pull()

censusDf |> filter(concept=="RACE") 

  

# Sex


# Race

# Age (use pyramid for this?)


```

Population and Growth, Anderson County and Municipalities, 1950 - 2020
Population Density, Anderson County and Municipalities, 2020 
Population by Sex, Race, and Age, Anderson County,
2010 and 2020
Population by Sex and Race, Anderson County and Municipalities,
2020

```{r}
totalOfEducation <- acsDf |> 
     filter(concept == "SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER" & NAME == "Anderson County" & cleanedLabel == "Total") |> pull()
acsDf |> 
     filter(concept == "SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER" & NAME == "Anderson County" & cleanedLabel != "Other") |> 
  mutate(pctOfEstimate = estimate/totalOfEducation) |> 
  select(-concept) |> 
  DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  caption = "IN-COMMUTING JOB COUNTS: ANDERSON COUNTY LABORERS BY COUNTIES WHERE LABORERS RESIDE",
  colnames = c('Place' = 'NAME', 'Level of Education' = 'cleanedLabel', 'Number of People' = 'estimate',
               'Percentage of People' = 'pctOfEstimate')
  ) |> 
  DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Number of People', currency = "", digits=0)

acsDf |> 
     filter(concept == "SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER") |> 
     ggplot(aes(x=cleanedLabel, y=estimate)) +
     geom_bar(stat="identity")
```
```{r}
#| title: Housing Units by Year of Construction

tmpDf <- acsDf |> filter(concept == "YEAR STRUCTURE BUILT") |> 
  pivot_wider(
    names_from = cleanedLabel,
    values_from = estimate
  ) |> 
  select(-year, -concept)
tmpDf |> 
  DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  caption = "Housing Units by Year of Construction",
  colnames = c('Place' = 'NAME')
  ) |> 
  DT::formatCurrency(which(sapply(tmpDf,is.numeric)), currency = "", digits=0)

acsDf |> filter(concept == "YEAR STRUCTURE BUILT" & cleanedLabel != "Total") |> 
  ggplot(aes(x=NAME, y=estimate, fill = cleanedLabel))+
  geom_bar(stat = "identity")

acsDf |> filter(concept == "YEAR STRUCTURE BUILT" &  cleanedLabel != "Total") |> 
  ggplot(aes(x=NAME, y=estimate, fill = cleanedLabel))+
  geom_bar(stat = "identity", position = "dodge")

acsDf |> filter(concept == "YEAR STRUCTURE BUILT" &  cleanedLabel != "Total") |> 
ggplot(aes(x = NAME,
           fill = cleanedLabel, y = estimate)) + 
  geom_bar(position = "fill", stat = "identity") +
  scale_y_continuous(breaks = seq(0, 1, .2)) +
  scale_fill_brewer(palette = "Set2") +
  labs(y = "Percent", 
       fill="Year Structure Built",
       x = "Place",
       title = "Year Structure Built by Place")
```

```{r}
#| title: Housing Units by Type of Tenure

tmpDf <- acsDf |> filter(concept == "TENURE") |> 
  pivot_wider(
    names_from = cleanedLabel,
    values_from = estimate
  ) |> 
  select(-year, -concept)
tmpDf |> 
  DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  caption = "Housing Units by Tenure Status",
  colnames = c('Place' = 'NAME')
  ) |> 
  DT::formatCurrency(which(sapply(tmpDf,is.numeric)), currency = "", digits=0)


acsDf |> filter(concept == "TENURE") |> 
  ggplot(aes(x=NAME, y= estimate, fill = cleanedLabel)) +
    geom_bar(position = position_dodge(preserve = "single"),stat="identity")
```

Educational Level of Persons 25 Years and Older, Anderson County and
State of Tennessee, 2019
Educational Level of Persons 25 Years and Older, Anderson County and
Municipalities, 2019
Housing Units by Year of Construction, Anderson County and Municipalities,
Pre 1939 - 2019
Housing Units by Type of Tenure, Anderson County and Municipalities,
2010 and 2019 

```{r}
totalJobs <- empData2010 |> 
  filter(workCountyName == "Anderson") |> 
  select(numberOfJobs) |> 
  summarize(sum(numberOfJobs)) |> 
  pull()

topFiveCounties <- empData2010 |> 
  filter(workCountyName == "Anderson") |> 
  # column_to_rownames(var="homeCountyName") |> 
  top_n(5) |> 
  select(homeCountyName) |> 
  pull()

empDataSubset <- empData2010 |> 
  filter(workCountyName == "Anderson") |> 
  mutate(
    homeCountyName=ifelse(homeCountyName %in% topFiveCounties, homeCountyName, "All Other Locations"),
    ) |> 
  group_by(homeCountyName) |> 
  summarize(
    numberOfJobs=sum(numberOfJobs),
    percentageOfJobs=numberOfJobs/totalJobs
    ) |> 
  ungroup() |> 
  mutate(isNotOther = ifelse(homeCountyName == "All Other Locations",0,1)) |> 
  arrange(desc(isNotOther),desc(numberOfJobs) ) |> 
    select(-isNotOther)
  
  
```

```{r}
#| title: TableOpt1
empDataSubset |> 
    gt(rowname_col = "homeCountyName") |>
   grand_summary_rows(
    columns=numberOfJobs,
    fns = 
      list(label = "Total In-Commuting Jobs", fn = "sum")
    ,
    fmt = ~ fmt_number(., use_seps = TRUE, decimals = 0)  
    ) |> 
  grand_summary_rows(
     columns=percentageOfJobs,
    fns = list(
      list(label = "Total In-Commuting Jobs", fn = "sum")
    ),
    fmt = ~ fmt_percent(., decimals = 0)
    ) |> 
  fmt_percent(
    columns = percentageOfJobs
  ) |> 
  fmt_number(
    columns = numberOfJobs,
    decimals = 0
  ) |> 
   tab_header(
    title = "IN-COMMUTING JOB COUNTS:
\nANDERSON COUNTY LABORERS
\nBY COUNTIES WHERE LABORERS RESIDE"
  ) |> 
    tab_options(
      heading.background.color = etddBlue,
      column_labels.background.color = etddBlue
    ) |> 
  tab_style(
    style = list(
      cell_borders(sides = "all", color = borderColor, weight = px(3))
    ),
    locations = list(
      cells_body(
      columns = everything()
    ),
    cells_column_labels()
  )
  ) |> 
  tab_style(style = cell_fill(color = lightStripe),
            locations = cells_body(rows = c(1, 3, 5))) |> 
  tab_style(style = cell_fill(color = medStripe),
            locations = cells_body(rows = c(2, 4, 6))) |> 
  tab_style(style = cell_fill(color = lightStripe),
            locations = cells_grand_summary()
  ) |> 
  tab_style(
      style = list(
        cell_fill(color = etddBlue),
        cell_text(color = colorForTextOnETDDBlue)
      ),
      locations = list(cells_stub(), cells_stub_grand_summary())
  )|>
   cols_label(
    numberOfJobs = "Job Count",
    percentageOfJobs = "Percentage",
    homeCountyName="Laborer’s County of Residence"
  )

```
### Economics
Income Comparison, Anderson County, State of Tennessee, and United States,
2009 and 2019
Income Comparison, Anderson County and Municipalities, 2019

Poverty Status of Families by Type, Anderson County, 2009 and 2019
Poverty Status of Families, Anderson County and Municipalities, 2019...................... 14
Table 10 Poverty Status of Female Householder Families, Anderson County and
Municipalities, 2019
Employment by Industry, Anderson County, 1960 - 2019 
Employment by Industry Anderson County and Municipalities, 2019
Labor Force by Place of Work, Anderson County, 1970 - 2019
Commuter Patterns, Anderson County, 2019
Labor Force by Place of Work, Anderson County and Municipalities, 2019

```{r}
#| title: "IN-COMMUTING JOB COUNTS: ANDERSON COUNTY LABORERS BY COUNTIES WHERE LABORERS RESIDE"
pctVars <- c("percentageOfJobs")
pctWholeVars <- c("")
total <- empDataSubset %>% 
      summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>% 
      mutate(homeCountyName = "Total")
empDataSubset |> 
  bind_rows(total) |> 
  #  mutate(across(any_of(pctVars), ~ 
  #                 str_c(
  #                   as.character(
  #                     round(
  #                       (ifelse(
  #                         str_detect(
  #                           .x,'Rate'),.x,.x*100
  #                         )
  #                        )
  #                       , digits=1)
  #                     )
  #                   , '%')
  #               )) %>% 
  # mutate(across(any_of(pctWholeVars), ~ 
  #                 str_c(
  #                   as.character(
  #                     .x
  #                     )
  #                   , '%')
  #               )) |> 
 DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  caption = "IN-COMMUTING JOB COUNTS: ANDERSON COUNTY LABORERS BY COUNTIES WHERE LABORERS RESIDE",
  colnames = c('Home County' = 'homeCountyName', 'Number of Jobs' = 'numberOfJobs', 'Percentage of Jobs' = 'percentageOfJobs')
  ) |> 
  DT::formatPercentage('Percentage of Jobs', 0) |> 
  DT::formatCurrency('Number of Jobs', currency = "", digits=0)
```

```{r}
(empDataSubset |> 
  ggplot(aes(x=homeCountyName,y=numberOfJobs, fill=homeCountyName)) +
  geom_bar(stat = "identity")+
  labs(x = "Home County", 
       y = "Number of Jobs", 
       title = "Number of Jobs by County")) |> 
  plotly::ggplotly()
  
```


# Blount

## Row
### Column{.tabset}
```{r}
totalJobs <- empData2010 |> 
  filter(workCountyName == "Anderson") |> 
  select(numberOfJobs) |> 
  summarize(sum(numberOfJobs)) |> 
  pull()

topFiveCounties <- empData2010 |> 
  filter(workCountyName == "Anderson") |> 
  # column_to_rownames(var="homeCountyName") |> 
  top_n(5) |> 
  select(homeCountyName) |> 
  pull()

empDataSubset <- empData2010 |> 
  filter(workCountyName == "Anderson") |> 
  mutate(
    homeCountyName=ifelse(homeCountyName %in% topFiveCounties, homeCountyName, "All Other Locations"),
    ) |> 
  group_by(homeCountyName) |> 
  summarize(
    numberOfJobs=sum(numberOfJobs),
    percentageOfJobs=numberOfJobs/totalJobs
    ) |> 
  ungroup() |> 
  mutate(isNotOther = ifelse(homeCountyName == "All Other Locations",0,1)) |> 
  arrange(desc(isNotOther),desc(numberOfJobs) ) |> 
    select(-isNotOther)
  
  
```

```{r}
#| title: TableOpt1
empDataSubset |> 
    gt(rowname_col = "homeCountyName") |>
   grand_summary_rows(
    columns=numberOfJobs,
    fns = 
      list(label = "Total In-Commuting Jobs", fn = "sum")
    ,
    fmt = ~ fmt_number(., use_seps = TRUE, decimals = 0)  
    ) |> 
  grand_summary_rows(
     columns=percentageOfJobs,
    fns = list(
      list(label = "Total In-Commuting Jobs", fn = "sum")
    ),
    fmt = ~ fmt_percent(., decimals = 0)
    ) |> 
  fmt_percent(
    columns = percentageOfJobs
  ) |> 
  fmt_number(
    columns = numberOfJobs,
    decimals = 0
  ) |> 
   tab_header(
    title = "IN-COMMUTING JOB COUNTS:
\nANDERSON COUNTY LABORERS
\nBY COUNTIES WHERE LABORERS RESIDE"
  ) |> 
    tab_options(
      heading.background.color = etddBlue,
      column_labels.background.color = etddBlue
    ) |> 
  tab_style(
    style = list(
      cell_borders(sides = "all", color = borderColor, weight = px(3))
    ),
    locations = list(
      cells_body(
      columns = everything()
    ),
    cells_column_labels()
  )
  ) |> 
  tab_style(style = cell_fill(color = lightStripe),
            locations = cells_body(rows = c(1, 3, 5))) |> 
  tab_style(style = cell_fill(color = medStripe),
            locations = cells_body(rows = c(2, 4, 6))) |> 
  tab_style(style = cell_fill(color = lightStripe),
            locations = cells_grand_summary()
  ) |> 
  tab_style(
      style = list(
        cell_fill(color = etddBlue),
        cell_text(color = colorForTextOnETDDBlue)
      ),
      locations = list(cells_stub(), cells_stub_grand_summary())
  )|>
   cols_label(
    numberOfJobs = "Job Count",
    percentageOfJobs = "Percentage",
    homeCountyName="Laborer’s County of Residence"
  )

```

```{r}
#| title: TableOpt2
pctVars <- c("percentageOfJobs")
pctWholeVars <- c("")
total <- empDataSubset %>% 
      summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>% 
      mutate(homeCountyName = "Total")
empDataSubset |> 
  bind_rows(total) |> 
  #  mutate(across(any_of(pctVars), ~ 
  #                 str_c(
  #                   as.character(
  #                     round(
  #                       (ifelse(
  #                         str_detect(
  #                           .x,'Rate'),.x,.x*100
  #                         )
  #                        )
  #                       , digits=1)
  #                     )
  #                   , '%')
  #               )) %>% 
  # mutate(across(any_of(pctWholeVars), ~ 
  #                 str_c(
  #                   as.character(
  #                     .x
  #                     )
  #                   , '%')
  #               )) |> 
 DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  colnames = c('Home County' = 'homeCountyName', 'Number of Jobs' = 'numberOfJobs', 'Percentage of Jobs' = 'percentageOfJobs')
  ) |> 
  DT::formatPercentage('Percentage of Jobs', 0)
```

```{r}

```

