---
title: | 
  ![](../resources/ETDDLogo.svg){width=1in} ETDD Census Data
logo:
    small: ../resources/ETDDLogo.svg
    medium: ../resources/ETDDLogo.svg
format: 
  dashboard: 
      css: ../resources/oddHighlight.css
      theme: 
        light: flatly
        dark: darkly
      scrolling: true
embed-resources: true
execute: 
  cache: true
params:
  refreshdata: FALSE
  county: "Anderson"
---

```{r initializing}
#| include: false
#| cache: true

if (exists("startrun")) {
  print(fortunes::fortune())
} else {
  source(here::here("Scripts","StartHere.r"))
}
if (exists("fxsVars")) {
  print(fortunes::fortune())
} else {
  source(here::here("scripts","fxsAndVars.R"))
}
source(here::here("scripts","defineColors.R"))

currentCounty <- params$county
currentMunicipalities <- paste0("municipalitiesIn",currentCounty)



if (file.exists(here::here("data","clean","odsCombined.csv")) & !refreshData) {
 empData2010 <- read_csv(here::here("data","clean","odsCombined.csv")) |> 
   filter(workCountyName == currentCounty | homeCountyName == currentCounty) |>
   select(-workPlaceName,-homePlaceName) |> 
   filter(!is.na(numberOfJobs))

 } else {
   
   source(here::here("scripts", "clean.R"))
   empData2010 <- read_csv(here::here("data","clean","odsCombined.csv"))  |>
    filter(workCountyName == currentCounty  | homeCountyName == currentCounty) |>
    filter(!is.na(numberOfJobs))

 }
totalWorkJobs <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  select(numberOfJobs) |> 
  summarize(sum(numberOfJobs)) |> 
  pull()
totalHomeJobs <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  select(numberOfJobs) |> 
  summarize(sum(numberOfJobs)) |> 
  pull()

topWorkCounties <- empData2010 |> 
  filter(workCountyName == currentCounty, year == currReportYear) |> 
  group_by(homeCountyName) |>
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(homeCountyName) |> 
  pull()

topHomeCounties <- empData2010 |> 
  filter(homeCountyName == currentCounty, year == currReportYear) |> 
  group_by(workCountyName) |>
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(workCountyName) |> 
  pull()

topOverallCounties <- empData2010 |> 
  pivot_longer(cols=c(-numberOfJobs,-year),values_to = "county") |> 
  group_by(county) |> 
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(county) |> 
  pull()

topCounties <- unique(c(topWorkCounties,topHomeCounties))

empDataWorkSubset <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  mutate(
    homeCountyName=ifelse(homeCountyName %in% topHomeCounties, homeCountyName, "All Other Locations"),
    ) |> 
  group_by(homeCountyName,year) |> 
  summarize(
    numberOfJobs=sum(numberOfJobs),
    percentageOfJobs=numberOfJobs/totalWorkJobs
    ) |> 
  ungroup() |> 
  mutate(isNotOther = ifelse(homeCountyName == "All Other Locations",0,1)) |> 
  arrange(desc(isNotOther),desc(numberOfJobs) ) |> 
    select(-isNotOther)
  
empDataHomeSubset <- empData2010 |> 
  filter(homeCountyName == currentCounty) |> 
  mutate(
    workCountyName=ifelse(workCountyName %in% topWorkCounties, workCountyName, "All Other Locations"),
    ) |> 
  group_by(workCountyName,year) |> 
  summarize(
    numberOfJobs=sum(numberOfJobs),
    percentageOfJobs=numberOfJobs/totalHomeJobs
    ) |> 
  ungroup() |> 
  mutate(isNotOther = ifelse(workCountyName == "All Other Locations",0,1)) |> 
  arrange(desc(isNotOther),desc(numberOfJobs) ) |> 
    select(-isNotOther)

totalWork <- empDataWorkSubset %>% 
      summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>% 
      mutate(homeCountyName = "Total",year=NA)
  
totalHome <- empDataHomeSubset %>% 
      summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>% 
      mutate(workCountyName = "Total",year=NA)
 

if (file.exists(here::here("data","clean","acsDataCombined.csv"))) {
 acsDf <- read_csv(here::here("data","clean","acsDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County")) 
} else {
  source(here::here("scripts", "clean.R"))
  acsDf <- read_csv(here::here("data","clean","acsDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County")) 
}
if (file.exists(here::here("data","clean","censusDataCombined.csv"))) {
 censusDf <- read_csv(here::here("data","clean","censusDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County"))
} else {
  source(here::here("scripts", "clean.R"))
  censusDf <- read_csv(here::here("data","clean","censusDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County"))
}


```

# Overview

## Row {.tabset}

### Overview of this product

### Description of the data and data sources

### Shiny App (to add later)

# Anderson

## Row {.tabset}
### Description

PUT MAP HERE

INTRODUCTION
This report is part of a series, which examines statistical data from U.S. Census materials regarding
economic and demographic characteristics in the sixteen counties that make up the East
Tennessee Development District. The series utilizes data from U.S. Decennial Censuses along with
American Community Survey Five-year Estimates as its primary sources. Please see the Data Description Tab for a detailed list of where the data comes from.

Topics that will be discussed in this summary report for Anderson County are
• population growth from 1950 to 2020;
• population density;
• demographic characteristics in terms of sex, race, and age;
• economic characteristics in terms of family income, household income, per capita income,
and poverty status of families;
• employment classification according to industry;
• labor force characteristics in terms of place of work and commuting patterns;
• educational level of the adult population;
• and housing characteristics in terms of age of the housing stock and type of tenure.

### Demographics{.tabset}

```{r}
#| title: Population and Growth
#| label: pop

censusDf |> filter(concept == "RACE", cleanedLabel=="Total") |> 
  ggplot(aes(x=year, y=value, color=NAME))+
  geom_point()

```


```{r}
#| title: Population Density
#| label: popDensity

placesShapeFile <- sf::read_sf(here::here("data","clean","tigerFiles2020place.gpkg"))
countiesShapeFile <- sf::read_sf(here::here("data","clean","tigerFiles2020county.gpkg"))

# (censusDf |> mutate(GEOID = as.character(GEOID))) |> left_join(countiesShapeFile) |> 
#   filter(concept=="Area") |> 
#   ggplot(aes(geometry=geom)) +
#   geom_sf()+
#     coord_sf(default_crs = NULL)

censusDf |> filter(cleanedLabel == "populationDensity") |> 
  ggplot(aes(x=NAME,y=value, fill = NAME))+
  geom_bar(stat='identity')
  
censusDf |> filter(cleanedLabel=="area" | cleanedLabel == "populationDensity") |> 
  pivot_wider(values_from = value, names_from = cleanedLabel) |> 
  select(-GEOID,-concept, -year) |> 
  DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  colnames = c('Place' = 'NAME', 'Population Density' = 'populationDensity','Area'='area')
  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Area', currency = "", digits=1) |> 
  DT::formatCurrency('Population Density', currency = "", digits=1)

```

```{r}
#| title: Population Descriptions
#| label: popDesc

censusDf |> 
  filter(concept=="RACE", cleanedLabel != "Total", !is.na(cleanedLabel)) |> 
  select(NAME, cleanedLabel, value) |> 
DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  colnames = c('Place' = 'NAME','Number of People' = 'value',
               'Race Category' = 'cleanedLabel')
  ) |> 
  DT::formatCurrency('Number of People', currency = "", digits=0)

acsDf |> 
  filter(concept=="AGE AND SEX") |> 
  filter(str_detect(cleanedLabel,"Total population")) |> 
  mutate(Sex = ifelse(str_detect(cleanedLabel,"Female"),"Female",
                      ifelse(str_detect(cleanedLabel,"Male"),"Male",NA)),
         AgeRange = str_remove(str_remove(str_remove(cleanedLabel, 
                                                     "FemaleTotal populationAGE"),
                                          "MaleTotal populationAGE"),
                               "TotalTotal populationAGE")
         ) |> 
  filter(!is.na(AgeRange)) |> 
  # pivot_wider(values_from = value, names_from = cleanedLabel) |> 
  select(NAME, Sex, AgeRange, year, estimate) |> 
  DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  colnames = c('Place' = 'NAME', 'Age Range' = 'AgeRange','Year'='year', 
               'Number of People' = 'estimate')
  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Number of People', currency = "", digits=0)
# Sex
  
acsDf |> filter(concept=="AGE AND SEX") |> filter(str_detect(cleanedLabel,"Total population")) |> 
  mutate(Sex = ifelse(str_detect(cleanedLabel,"Female"),"Female",
                      ifelse(str_detect(cleanedLabel,"Male"),"Male",NA)),
         AgeRange = str_remove(str_remove(str_remove(cleanedLabel, 
                                                     "FemaleTotal populationAGE"),
                                          "MaleTotal populationAGE"),
                               "TotalTotal populationAGE"),
         estimate=ifelse(Sex == "Female", -estimate, estimate)
         ) |> 
    filter(!is.na(AgeRange), !is.na(Sex)) |> 
  ggplot(
    aes(
      x = estimate,
      y = AgeRange,
      fill = Sex
    )
  ) +
  geom_col() +
  geom_label(
    aes(
      x = 0,
      label = AgeRange
    ),
    fill = "white",
    label.size = 0
  )

# Race
censusDf |> filter(concept=="RACE", cleanedLabel != "Total", !is.na(cleanedLabel)) |> 
  ggplot(aes(x=cleanedLabel, y=value))+
  geom_bar(stat="identity")

# Age (use pyramid for this?)


```

```{r}
#| title: Education
#| label: edu

totalOfEducation <- acsDf |> 
     filter(concept == "SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER" & cleanedLabel == "Total") |> pull()
acsDf |> 
     filter(concept == "SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER"  & cleanedLabel != "Other") |> 
  mutate(pctOfEstimate = estimate/totalOfEducation) |> 
  select(-concept) |> 
  DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  colnames = c('Place' = 'NAME', 'Level of Education' = 'cleanedLabel', 'Number of People' = 'estimate',
               'Percentage of People' = 'pctOfEstimate')
  ) |> 
  DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Number of People', currency = "", digits=0)

acsDf |> 
     filter(concept == "SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER") |> 
     ggplot(aes(x=cleanedLabel, y=estimate)) +
     geom_bar(stat="identity")
```
```{r}
#| title: Housing Units by Year of Construction
#| label: constYear

tmpDf <- acsDf |> filter(concept == "YEAR STRUCTURE BUILT") |> 
  pivot_wider(
    names_from = cleanedLabel,
    values_from = estimate
  ) |> 
  select(-year, -concept)
tmpDf |> 
  DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  caption = "Housing Units by Year of Construction",
  colnames = c('Place' = 'NAME')
  ) |> 
  DT::formatCurrency(which(sapply(tmpDf,is.numeric)), currency = "", digits=0)

acsDf |> filter(concept == "YEAR STRUCTURE BUILT" & cleanedLabel != "Total") |> 
  ggplot(aes(x=NAME, y=estimate, fill = cleanedLabel))+
  geom_bar(stat = "identity")

acsDf |> filter(concept == "YEAR STRUCTURE BUILT" &  cleanedLabel != "Total") |> 
  ggplot(aes(x=NAME, y=estimate, fill = cleanedLabel))+
  geom_bar(stat = "identity", position = "dodge")

acsDf |> filter(concept == "YEAR STRUCTURE BUILT" &  cleanedLabel != "Total") |> 
ggplot(aes(x = NAME,
           fill = cleanedLabel, y = estimate)) + 
  geom_bar(position = "fill", stat = "identity") +
  scale_y_continuous(breaks = seq(0, 1, .2)) +
  scale_fill_brewer(palette = "Set2") +
  labs(y = "Percent", 
       fill="Year Structure Built",
       x = "Place",
       title = "Year Structure Built by Place")
```

```{r}
#| title: Housing Units by Type of Tenure
#| label: tenureType

tmpDf <- acsDf |> filter(concept == "TENURE") |> 
  pivot_wider(
    names_from = cleanedLabel,
    values_from = estimate
  ) |> 
  select(-year, -concept)
tmpDf |> 
  DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  caption = "Housing Units by Tenure Status",
  colnames = c('Place' = 'NAME')
  ) |> 
  DT::formatCurrency(which(sapply(tmpDf,is.numeric)), currency = "", digits=0)


acsDf |> filter(concept == "TENURE") |> 
  ggplot(aes(x=NAME, y= estimate, fill = cleanedLabel)) +
    geom_bar(position = position_dodge(preserve = "single"),stat="identity")
```

### Economics{.tabset}

```{r}
#| title: Income comparison
#| label: income

acsDf |> 
  filter(concept == "PER CAPITA INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)") |> 
  select(NAME,estimate,year) |> 
  DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  colnames = c('Place' = 'NAME', 'Year'='year', 
               'Income' = 'estimate')
  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Income', currency = "", digits=0)

acsDf |> 
  filter(concept == "PER CAPITA INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)") |> 
  ggplot(aes(x=estimate, y=reorder(NAME, estimate))) +
  geom_point(color="blue", size = 2) +
  geom_segment(aes(x = 40, 
               xend = estimate, 
               y = reorder(NAME, estimate), 
               yend = reorder(NAME, estimate)),
               color = "lightgrey") +
  labs (x = "Income (per capita)",
        y = "",
        title = "Income by Municipality",
        subtitle = "(Anderson County)") +
  theme_minimal() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
```

```{r}
#| title: Poverty Status
#| label: poverty
acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel == "Above Poverty" | cleanedLabel == "Below Poverty") |> 
  select(NAME,cleanedLabel,year,estimate) |> 
  pivot_wider(names_from = cleanedLabel,values_from = estimate) |> 
DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  colnames = c('Place' = 'NAME', 'Year'='year')
  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Above Poverty', currency = "", digits=0) |> 
  DT::formatCurrency('Below Poverty', currency = "", digits=0)

acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel != "Other") |> 
  ggplot(aes(x=NAME, y=estimate, fill=cleanedLabel))+
  geom_bar(stat = "identity", position = "dodge")

```

```{r}
#| title: Poverty Status by Family Type
#| label: povertyFamily

# All Families, Families Headed by Females, Headed by Female with Related Children under 18
acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel != "Other", cleanedLabel != "Total") |> 
  select(NAME,cleanedLabel,year,estimate) |> 
  mutate(`Poverty Status` = ifelse(str_detect(cleanedLabel,"Above Poverty"),"Above Poverty","Below Poverty"),
         `Family Type` = case_when(
           str_detect(cleanedLabel, "Female Householder with related children")
           ~ "Female Householder with related children",
           str_detect(cleanedLabel,"Female Householder")
           ~ "Female Householder",
           .default="All Families"
         )
  ) |> 
  select(-cleanedLabel) |>
  relocate(estimate, .after = last_col()) |> 
  relocate(year, .after = last_col()) |> 
  # pivot_wider(names_from = cleanedLabel,values_from = estimate) |> 
DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  colnames = c('Place' = 'NAME', 'Year'='year', 'Number of Families'='estimate')
  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  # DT::formatCurrency('Above Poverty', currency = "", digits=0) |> 
  DT::formatCurrency('Number of Families', currency = "", digits=0)

acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel != "Other") |> 
  select(NAME,cleanedLabel,year,estimate) |> 
   mutate(`Poverty Status` = ifelse(str_detect(cleanedLabel,"Above Poverty"),"Above Poverty","Below Poverty"),
         `Family Type` = case_when(
           str_detect(cleanedLabel, "Female Householder with related children")
           ~ "Female Householder with related children",
           str_detect(cleanedLabel,"Female Householder")
           ~ "Female Householder",
           .default="All Families"
         )
  ) |> 
  ggplot(aes(x=`Poverty Status`,y=estimate,fill=`Family Type`))+
  geom_bar(stat="identity", position="stack")
```

```{r}
#| title: Employment by Industry
#| label: emp

acsDf |> filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other" & cleanedLabel != "EstimateTotal" & cleanedLabel != "Total") |> 
  mutate(cleanedLabel = str_remove(cleanedLabel,"([\\w\\s\\,]*:)")) |> 
  select(-concept) |> 
DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  colnames = c('Place' = 'NAME', 'Year'='year', 'Number of Jobs' = 'estimate')
  ) |> 
  DT::formatCurrency('Number of Jobs', currency='', digits=0)

plotly::ggplotly(
acsDf |> filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other" & cleanedLabel != "EstimateTotal" & cleanedLabel != "Total") |> 
  ggplot(aes(x=estimate, y=NAME, color = cleanedLabel))+
  geom_jitter()+
  theme(legend.position = "none"))

plotly::ggplotly(
acsDf |> filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other" & cleanedLabel != "EstimateTotal" & cleanedLabel != "Total") |> 
  ggplot(aes(x=estimate, y=NAME, fill = cleanedLabel))+
  geom_bar(stat = "identity", position = "dodge")+
  theme(legend.position = "none"))

```


```{r}
#| title: Employment by Industry (Historical)
#| label: empHist

acsDf |> filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other" & cleanedLabel != "EstimateTotal" & cleanedLabel != "Total") |> 
  mutate(cleanedLabel = str_remove(cleanedLabel,"(:[\\w\\s,&]*)")) |> 
  select(-concept) |> 
  group_by(NAME,year,cleanedLabel) |> 
  summarize(estimate=sum(estimate)) |> 
DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  colnames = c('Place' = 'NAME', 'Year'='year', 'Number of Jobs' = 'estimate')
  ) |> 
  DT::formatCurrency('Number of Jobs', currency='', digits=0)

```


```{r}
#| title: Labor Force by Place of Work
#| label: placeWork

acsDf |> 
  filter(concept=="MEANS OF TRANSPORTATION TO WORK BY PLACE OF WORK--STATE AND COUNTY LEVEL", cleanedLabel!="Other", cleanedLabel !="Total") |>
  select(-concept) |> 
  pivot_wider(values_from = estimate,names_from = cleanedLabel) |> 
  
DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  colnames = c('Place' = 'NAME', 'Year'='year')
  ) |> 
  DT::formatCurrency('Work Out Of State', currency='', digits=0) |> 
  DT::formatCurrency('Work Out of County of Residence', currency='', digits=0) |> 
  DT::formatCurrency('Work in County of Residence', currency='', digits=0) 


acsDf |> filter(concept=="MEANS OF TRANSPORTATION TO WORK BY PLACE OF WORK--STATE AND COUNTY LEVEL", cleanedLabel!="Other") |> 
  ggplot(aes(x=cleanedLabel,y=estimate,fill=cleanedLabel))+
  geom_bar(stat="identity")

```


```{r}
#| title: Commuting Patterns
#| label: commuting

pctVars <- c("percentageOfJobs")
pctWholeVars <- c("")

empDataWorkSubset |> 
  bind_rows(totalWork) |> 
 DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  caption = "Anderson County laborers by counties where laborers reside",
  colnames = c('Home County' = 'homeCountyName', 'Number of Jobs' = 'numberOfJobs', 'Percentage of Jobs' = 'percentageOfJobs')
  ) |> 
  DT::formatPercentage('Percentage of Jobs', 0) |> 
  DT::formatCurrency('Number of Jobs', currency = "", digits=0)

(empDataWorkSubset |> 
  ggplot(aes(x=homeCountyName,y=numberOfJobs, fill=homeCountyName)) +
  geom_bar(stat = "identity")+
  labs(x = "Home County", 
       y = "Number of Jobs", 
       title = "Number of Jobs by County")) |> 
  plotly::ggplotly()

empDataHomeSubset |> 
  bind_rows(totalHome) |> 
 DT::datatable(
    filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    ),
  caption = "Anderson County residents by counties where residents work",
  colnames = c('Work County' = 'workCountyName', 'Number of Jobs' = 'numberOfJobs', 'Percentage of Jobs' = 'percentageOfJobs')
  ) |> 
  DT::formatPercentage('Percentage of Jobs', 0) |> 
  DT::formatCurrency('Number of Jobs', currency = "", digits=0)

(empDataHomeSubset |> 
  ggplot(aes(x=workCountyName,y=numberOfJobs, fill=workCountyName)) +
  geom_bar(stat = "identity")+
  labs(x = "Work County", 
       y = "Number of Jobs", 
       title = "Number of Jobs by County")) |> 
  plotly::ggplotly()
```



# Blount
```{r}

```

