---
title: | 
  ![](../resources/ETDDLogo.svg){width=1in} ETDD Census Data
logo:
    small: ../resources/ETDDLogo.svg
    medium: ../resources/ETDDLogo.svg
format: 
  dashboard: 
      orientation: rows
      css: ../resources/oddHighlight.css
      theme: 
        light: flatly
        dark: darkly
      scrolling: true
embed-resources: true
execute: 
  cache: true
params:
  refreshdata: FALSE
  county: "Anderson"
  tableIdStart: 1
---

```{r initializing}
#| include: false
#| cache: false

refreshData <- params$refreshdata
tableId <- params$tableIdStart
if (exists("startrun")) {
  print(fortunes::fortune())
} else {
  source(here::here("Scripts","StartHere.r"))
}
if (exists("fxsVars")) {
  print(fortunes::fortune())
} else {
  source(here::here("scripts","fxsAndVars.R"))
}
source(here::here("scripts","defineColors.R"))

currentCounty <- params$county
currentMunicipalities <- paste0("municipalitiesIn",currentCounty)



if (file.exists(here::here("data","clean","odsCombined.csv")) & !refreshData) {
 empData2010 <- read_csv(here::here("data","clean","odsCombined.csv")) |> 
   filter(workCountyName == currentCounty | homeCountyName == currentCounty) |>
   select(-workPlaceName,-homePlaceName) |> 
   filter(!is.na(numberOfJobs))

 } else {
   
   source(here::here("scripts", "clean.R"))
   empData2010 <- read_csv(here::here("data","clean","odsCombined.csv"))  |>
    filter(workCountyName == currentCounty  | homeCountyName == currentCounty) |>
    filter(!is.na(numberOfJobs))

 }
totalWorkJobs <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  select(numberOfJobs) |> 
  summarize(sum(numberOfJobs)) |> 
  pull()
totalHomeJobs <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  select(numberOfJobs) |> 
  summarize(sum(numberOfJobs)) |> 
  pull()

topWorkCounties <- empData2010 |> 
  filter(workCountyName == currentCounty, year == currReportYear) |> 
  group_by(homeCountyName) |>
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(homeCountyName) |> 
  pull()

topHomeCounties <- empData2010 |> 
  filter(homeCountyName == currentCounty, year == currReportYear) |> 
  group_by(workCountyName) |>
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(workCountyName) |> 
  pull()

topOverallCounties <- empData2010 |> 
  pivot_longer(cols=c(-numberOfJobs,-year),values_to = "county") |> 
  group_by(county) |> 
  summarize(numberOfJobs=sum(numberOfJobs)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopCounties) |> 
  select(county) |> 
  pull()

topCounties <- unique(c(topWorkCounties,topHomeCounties))

empDataWorkSubset <- empData2010 |> 
  filter(workCountyName == currentCounty) |> 
  mutate(
    homeCountyName=ifelse(homeCountyName %in% topHomeCounties, homeCountyName, "All Other Locations"),
    ) |> 
  group_by(homeCountyName,year) |> 
  summarize(
    numberOfJobs=sum(numberOfJobs),
    percentageOfJobs=numberOfJobs/totalWorkJobs
    ) |> 
  ungroup() |> 
  mutate(isNotOther = ifelse(homeCountyName == "All Other Locations",0,1)) |> 
  arrange(desc(isNotOther),desc(numberOfJobs) ) |> 
    select(-isNotOther)
  
empDataHomeSubset <- empData2010 |> 
  filter(homeCountyName == currentCounty) |> 
  mutate(
    workCountyName=ifelse(workCountyName %in% topWorkCounties, workCountyName, "All Other Locations"),
    ) |> 
  group_by(workCountyName,year) |> 
  summarize(
    numberOfJobs=sum(numberOfJobs),
    percentageOfJobs=numberOfJobs/totalHomeJobs
    ) |> 
  ungroup() |> 
  mutate(isNotOther = ifelse(workCountyName == "All Other Locations",0,1)) |> 
  arrange(desc(isNotOther),desc(numberOfJobs) ) |> 
    select(-isNotOther)

totalWork <- empDataWorkSubset %>% 
      summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>% 
      mutate(homeCountyName = "Total",year=NA)
  
totalHome <- empDataHomeSubset %>% 
      summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>% 
      mutate(workCountyName = "Total",year=NA)
 

if (file.exists(here::here("data","clean","acsDataCombined.csv"))) {
 acsDf <- read_csv(here::here("data","clean","acsDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County")) 
} else {
  source(here::here("scripts", "clean.R"))
  acsDf <- read_csv(here::here("data","clean","acsDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County")) 
}
if (file.exists(here::here("data","clean","ipumsPop.csv"))) {
 pumsPopDf <- read_csv(here::here("data","clean","ipumsPop.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County")) 
} else {
  source(here::here("scripts", "clean.R"))
  pumsPopDf <- read_csv(here::here("data","clean","ipumsPop.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County")) 
}

if (file.exists(here::here("data","clean","censusDataCombined.csv"))) {
 censusDf <- read_csv(here::here("data","clean","censusDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County"))
} else {
  source(here::here("scripts", "clean.R"))
  censusDf <- read_csv(here::here("data","clean","censusDataCombined.csv")) |> filter(NAME %in% get(currentMunicipalities) | NAME == str_c(currentCounty," County"))
}

theme_set(theme_classic())
scale_colour_discrete <- scale_colour_viridis_d
options(ggplot2.continuous.colour="mako")
options(ggplot2.continuous.fill = "mako")
options(ggplot2.discrete.colour = "mako_d")
options(ggplot2.discrete.fill = "mako_d")
options(ggplot2.ordinal.colour = "mako")
options(ggplot2.ordinal.fill = "mako")
scale_fill_discrete <- function(...) {
   #scale_fill_manual(..., values = viridis_qualitative_pal7)
  viridis::scale_fill_viridis(discrete = TRUE, option="G")
} 
options(DT.options = list(filter="top",
    extensions = c('Buttons', 
     'FixedHeader'),
    options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'print'),
    scrollX = TRUE,
   fixedHeader=TRUE,
  initComplete = DT::JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#015a71', 'color': '#fff'});",
    "}")
    )))
```

# Overview

## Column {.tabset}

### Overview of this product

### Description of the data and data sources

### Shiny App (to add later)

# Anderson

## Column {.tabset}
### Description

PUT MAP HERE

INTRODUCTION
This report is part of a series, which examines statistical data from U.S. Census materials regarding
economic and demographic characteristics in the sixteen counties that make up the East
Tennessee Development District. The series utilizes data from U.S. Decennial Censuses along with
American Community Survey Five-year Estimates as its primary sources. Please see the Data Description Tab for a detailed list of where the data comes from.

Topics that will be discussed in this summary report for Anderson County are
• population growth from 1950 to 2020;
• population density;
• demographic characteristics in terms of sex, race, and age;
• economic characteristics in terms of family income, household income, per capita income,
and poverty status of families;
• employment classification according to industry;
• labor force characteristics in terms of place of work and commuting patterns;
• educational level of the adult population;
• and housing characteristics in terms of age of the housing stock and type of tenure.

### Demographics {.tabset}

#### Population and Growth 
::::{.columns}
```{r}
#| label: popTable
varsWithoutAComma <- pumsPopDf |> select(-NAME) |> names()
pumsPopDf |> 
  DT::datatable(
    caption = "IPUMS NHGIS, University of Minnesota, www.nhgis.org ",
  colnames = c('Place' = 'NAME'),
  elementId = paste0("DataTables_",tableId)
  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency(varsWithoutAComma, currency = "", digits=1)
tableId <- tableId+1
```
```{r}
#| label: popGraph

plotly::ggplotly(
  

pumsPopDf |> 
  pivot_longer(
    cols = c(-NAME,-starts_with("Change")),
    names_to = "year",
    values_to = "population"
  ) |> 
  mutate(year=factor(year)) |> 
  select(-starts_with("Change")) |> 
  filter(!is.na(population)) |> 
  ggplot( aes(x = year,
                     y = population, 
                     color = NAME,
              group=NAME)) +
  geom_line()+
  labs(
    caption = "IPUMS NHGIS, University of Minnesota, www.nhgis.org ",
    color="Place",
    y="Population"
  ) +
  scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )
)
```
:::::

#### Population Density 

:::: {.columns}


```{r}
#| label: popDensityTable
censusDf |> filter(cleanedLabel=="area" | cleanedLabel == "populationDensity") |> 
  pivot_wider(values_from = value, names_from = cleanedLabel) |> 
  mutate(NAME=ifelse(NAME=="Rocky Top","Rocky Top(a)",NAME)) |> 
  select(-GEOID,-concept, -year) |> 
  DT::datatable(
    caption = "Density is population / area (in square miles) \\n (a) Formerly Lake City",
  colnames = c('Place' = 'NAME', 'Population Density' = 'populationDensity','Area'='area'),
    elementId = paste0("DataTables_",tableId)

  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Area', currency = "", digits=1) |> 
  DT::formatCurrency('Population Density', currency = "", digits=1)
tableId <- tableId+1
```
```{r}
#| label: popDensityFig

placesShapeFile <- sf::read_sf(here::here("data","clean","tigerFiles2020place.gpkg"))
countiesShapeFile <- sf::read_sf(here::here("data","clean","tigerFiles2020county.gpkg"))

# (censusDf |> mutate(GEOID = as.character(GEOID))) |> left_join(countiesShapeFile) |> 
#   filter(concept=="Area") |> 
#   ggplot(aes(geometry=geom)) +
#   geom_sf()+
#     coord_sf(default_crs = NULL)

censusDf |> filter(cleanedLabel == "populationDensity") |> 
  ggplot(aes(x=NAME,y=value))+
  geom_bar(stat='identity', fill=barColor,color=barOutlineColor)+
  labs(y="Population Density",
       x="",
       caption = "Density is population/area(in square miles)")+
  scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )
  

```
::::


#### Population Descriptions
:::: {.columns}
:::{.row}
```{r}
#| label: popDescRaceTable
pctVarName <- "Percentage of People"
max_num <- acsDf |> 
  filter(concept=="AGE AND SEX") |> 
  filter(str_detect(cleanedLabel,"Total population"), !str_detect(cleanedLabel,"TotalTotal")) |> 
  select(estimate) |> 
  slice_max(
    order_by = estimate,
    n = 1
  ) |>
  pull(estimate)

popPyramidData <- acsDf |> filter(concept=="AGE AND SEX") |> filter(str_detect(cleanedLabel,"Total population")) |> 
  mutate(Sex = ifelse(str_detect(cleanedLabel,"Female"),"Female",
                      ifelse(str_detect(cleanedLabel,"Male"),"Male",NA)),
         AgeRange = str_remove(str_remove(str_remove(cleanedLabel, 
                                                     "FemaleTotal populationAGE"),
                                          "MaleTotal populationAGE"),
                               "TotalTotal populationAGE"),
         estimate=ifelse(Sex == "Female", -estimate, estimate),
         AgeRange=factor(AgeRange, levels=c("Under 5 years",
                                               "5 to 9 years",
                                               "10 to 14 years", 
                                                "15 to 19 years",   
                                                "20 to 24 years",   
                                                "25 to 29 years",   
                                                "30 to 34 years",   
                                                "35 to 39 years",   
                                                "40 to 44 years",   
                                                "45 to 49 years",   
                                                "50 to 54 years",   
                                                "55 to 59 years",   
                                                "60 to 64 years",   
                                                "65 to 69 years",   
                                                "70 to 74 years",   
                                                "75 to 79 years",   
                                                "80 to 84 years",   
                                                "85 years and over"
                                               ))
         ) |> 
  rbind(
    acsDf |> 
      filter(concept=="AGE AND SEX") |> 
      filter(str_detect(cleanedLabel,"Total population"),str_detect(cleanedLabel,"TotalTotal")) |> 
      group_by(NAME,concept,year) |> summarize(estimate=sum(estimate)) |>   
      mutate(cleanedLabel="Total",AgeRange=NA,Sex=NA)
  ) |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2020, valueVarName="estimate") |> 
  mutate(`Percentage of People` = abs(`Percentage of People`)) |> 
    filter(!is.na(AgeRange), !is.na(Sex)) 


censusDf |> 
  filter(concept=="RACE", !is.na(cleanedLabel)) |>
  addPercentVar(pctVarName, totalVarValue="Total", year=2020, valueVarName="value") |> 
  filter( cleanedLabel != "Total") |> 
  select(NAME, year, cleanedLabel, value, any_of(pctVarName)) |> 
DT::datatable(
  colnames = c('Place' = 'NAME','Number of People' = 'value',
               'Race Category' = 'cleanedLabel'),
    elementId = paste0("DataTables_",tableId)
  ) |> 
  DT::formatCurrency('Number of People', currency = "", digits=0) |> 
  DT::formatPercentage(pctVarName, digits=2)
tableId <- tableId+1
```
``` {r}
#| label: popAgeTable
 
popPyramidData |> 
  # pivot_wider(values_from = value, names_from = cleanedLabel) |> 
  select(NAME, Sex, AgeRange, year, estimate, pctVarName) |> 
  mutate(estimate=abs(estimate)) |> 
  DT::datatable(
  colnames = c('Place' = 'NAME', 'Age Range' = 'AgeRange','Year'='year', 
               'Number of People' = 'estimate'),
    elementId = paste0("DataTables_",tableId)

  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Number of People', currency = "", digits=0) |> 
  DT::formatPercentage(pctVarName, digits=2)
# Sex
  tableId <- tableId+1
```
::::

:::{.row}
```{r}
#| label: popRaceGraph
censusDf |> filter(concept=="RACE", cleanedLabel != "Total", !is.na(cleanedLabel)) |> 
  ggplot(aes(x=cleanedLabel, y=value, fill=NAME))+
  geom_bar(stat="identity",position="dodge")+
  labs(
    x="Racial Category",
    y="Estimated Population",
    fill="Place"
  )+
  scale_y_continuous(
    labels = scales::comma,
    breaks = breaks_pretty()
  )

```



``` {r}
#| label: popPyramid
population_pyramid_men <- popPyramidData |>
  filter(Sex == "Male", NAME==currentCounty) |>
  ggplot(aes(
    x = estimate,
    y = AgeRange
    
  )) +
  geom_col(fill=etddBlueDark)+
  annotate(
    geom = "label",
    x = 2*(max_num/3),
    y = 17,
    label = "Male",
    fill = etddBlueDark,
    color = "white",
    label.padding = unit(0.3, "lines")
  ) +
  scale_x_continuous(
    labels = scales::comma,
    breaks = breaks_pretty(),
    limits = c(0, max_num)
  ) +
  labs(x="",y="", caption=str_c("data for ", currentCounty))+
  theme(
    axis.title.y=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.x = element_text(),
    axis.line.y= element_blank(),
    panel.grid.major.x = element_line(color = "grey90")
  )
population_pyramid_women <-
  popPyramidData |>
  filter(Sex == "Female",NAME==currentCounty) |>
  ggplot(aes(
    x = estimate,
    y = AgeRange
   
  )) +
  geom_col(fill = etddGreen) +
  annotate(
    geom = "label",
    x =  -(2*(max_num/3)),
    y = 17,
    label = "Female",
    fill = etddGreen,
    color = "grey30",
    
    label.padding = unit(0.3, "lines")
  ) +
  scale_x_continuous(
    labels = function(x) scales::comma(abs(x)),
    breaks = breaks_pretty(),
    limits = c(-max_num, 0)
  ) +
  labs(x="",y="")+
  theme(
    axis.title.y=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.text.x = element_text(),
    axis.line.y= element_blank(),
    panel.grid.major.x = element_line(color = "grey90")
  )

  age_labels_plot <-
  popPyramidData |> 
    select(AgeRange) |> distinct() |> 
  ggplot(
    aes(
      x = 1,
      y = AgeRange,
      label = AgeRange
    )
  ) +
  geom_text() +
  theme_void()
  
  population_pyramid_women +
  age_labels_plot +
  population_pyramid_men +
  plot_layout(
    widths = c(7.5, 3.5, 7.5)
  )
# Race

# Age (use pyramid for this?)


```
::::
:::::
#### Education
::::{.columns}
```{r}
#| label: eduTable

acsDf |> 
  filter(concept == "SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER"  &
           cleanedLabel != "Other") |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2020) |>
  addPercentVar(pctVarName, totalVarValue="Total", year=2010) |>
  select(-concept) |> 
  DT::datatable(
  colnames = c('Place' = 'NAME', 'Level of Education' = 'cleanedLabel', 'Number of People' = 'estimate', 'Year'='year'),
    elementId = paste0("DataTables_",tableId)
  ) |> 
  DT::formatPercentage(pctVarName, 0) |>
  DT::formatCurrency('Number of People', currency = "", digits=0)
tableId <- tableId+1
```

```{r}
#| label: eduGraph
plotly::ggplotly(
acsDf |> 
     filter(concept == "SEX BY EDUCATIONAL ATTAINMENT FOR THE POPULATION 25 YEARS AND OVER", cleanedLabel!="Other",cleanedLabel!="Total") |> 
  mutate(cleanedLabel = factor(cleanedLabel, levels=c(
    "Less Than 9th Grade",
    "9th to 12th Grade, No Diploma",
    "Some College, No Degree",
    "Associate's degree",
    "Bachelor's degree",
    "Graduate or Professional Degree"
  ))) |> 
     ggplot(aes(x=cleanedLabel, y=estimate, fill=NAME)) +
     geom_bar(stat="identity", position="dodge")+
  labs(x="Estimated Population",y="Education Category", fill="Place")+
  scale_y_continuous(
    labels = scales::comma,
    breaks = breaks_pretty()
  )
)
```
:::::
#### Housing Units by Year of Construction
::::{.columns}
```{r}
#| label: constYearTable
tmpDf <- acsDf |> filter(concept == "YEAR STRUCTURE BUILT") |> 
  pivot_wider(
    names_from = cleanedLabel,
    values_from = estimate
  ) |> 
  select(-concept)
varsWithAComma <- tmpDf |>  select(-NAME,-year) |> names()

tmpDf |> 
  DT::datatable(
    caption = "Housing Units by Year of Construction",
  colnames = c('Place' = 'NAME'),
    elementId = paste0("DataTables_",tableId)

  ) |> 
  DT::formatCurrency(varsWithAComma, currency = "", digits=0)
tableId <- tableId+1
```

```{r}
#| label: constYearGraph

acsDf |> 
 filter(concept == "YEAR STRUCTURE BUILT" & cleanedLabel != "Total", cleanedLabel !="EstimateTotal") |> 
  mutate(cleanedLabel=str_remove(cleanedLabel,"EstimateTotalBuilt ")) |> 
ggplot(aes(x = NAME,
           fill = cleanedLabel, y = estimate)) + 
  geom_bar(position = "fill", stat = "identity") +
  labs(y = "Percent", 
       fill="Year Structure Built",
       x = "",
       title = "Year Structure Built by Place")+
   scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::percent,
     breaks=pretty_breaks()
   )

```
:::::
#### Housing Units by Type of Tenure
::::{.columns}
```{r}
#| label: tenureTypeTable

tmpDf <- acsDf |> filter(concept == "TENURE") |> 
  pivot_wider(
    names_from = cleanedLabel,
    values_from = estimate
  ) |> 
  select(-concept)
tmpDf |> 
  DT::datatable(
    
  caption = "Housing Units by Tenure Status",
  colnames = c('Place' = 'NAME'),
    elementId = paste0("DataTables_",tableId)

  ) |> 
  DT::formatCurrency(which(sapply(tmpDf,is.numeric)), currency = "", digits=0)
tableId <- tableId+1
```

```{r}
#| label: tenureTypeGraph
acsDf |> filter(concept == "TENURE") |> 
  ggplot(aes(x=NAME, y= estimate, fill = cleanedLabel)) +
    geom_bar(position = position_dodge(preserve = "single"),stat="identity")+
  labs(y="Estimated Number of Houses",
       x="",
       fill="Type of Tenure")+
  scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )
```
:::::

### Economics{.tabset}
#### Income Comparison
::::{.columns}
```{r}
#| label: incomeTable
varsWithAComma <- acsDf |> 
  filter(concept == "PER CAPITA INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)" | concept == "INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)", cleanedLabel != "Other") |> 
   select(-concept) |> 
  pivot_wider(values_from = estimate,names_from = cleanedLabel) |> select(-NAME,-year) |> names()

acsDf |> 
  filter(concept == "PER CAPITA INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)" | concept == "INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)", cleanedLabel != "Other") |> 
   select(-concept) |> 
  pivot_wider(values_from = estimate,names_from = cleanedLabel)|> 
  DT::datatable(
  colnames = c('Place' = 'NAME', 'Year'='year'),
    elementId = paste0("DataTables_",tableId)

  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency(varsWithAComma, currency = "", digits=0)
tableId <- tableId+1
```

``` {r}
#| label: incomeGraph
acsDf |> 
  filter(concept == "PER CAPITA INCOME IN THE PAST 12 MONTHS (IN 2020 INFLATION-ADJUSTED DOLLARS)") |> 
  ggplot(aes(x=estimate, y=reorder(NAME, estimate))) +
  geom_point(color="blue", size = 2) +
  geom_segment(aes(x = 40, 
               xend = estimate, 
               y = reorder(NAME, estimate), 
               yend = reorder(NAME, estimate)),
               color = "lightgrey") +
  labs (x = "Income (per capita)",
        y = "",
        title = "Income by Municipality",
        subtitle = "(Anderson County)") +
  theme_minimal() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
   scale_x_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )
```
:::::

#### Povery Status
::::{.columns}
```{r}
#| label: povertyTable
acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel == "Above Poverty" | cleanedLabel == "Below Poverty") |> 
  select(NAME,cleanedLabel,year,estimate) |> 
  pivot_wider(names_from = cleanedLabel,values_from = estimate) |> 
DT::datatable(
    colnames = c('Place' = 'NAME', 'Year'='year'),
      elementId = paste0("DataTables_",tableId)

  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  DT::formatCurrency('Above Poverty', currency = "", digits=0) |> 
  DT::formatCurrency('Below Poverty', currency = "", digits=0)
tableId <- tableId+1
```

```{r}
#| label: povertyGraph
acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel == "Above Poverty" | cleanedLabel == "Below Poverty") |> 
  ggplot(aes(x=NAME, y=estimate, fill=cleanedLabel))+
  geom_bar(stat = "identity", position = "dodge")+
  labs(y="Estimated Number of Families",
       x="",
       fill="Poverty Status")+
  scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )
  

```
:::::

#### Poverty Status by Family Type
::::{.columns}
```{r}
#| label: povertyFamilyTable
pctVarName = "Percentage of Families"
# All Families, Families Headed by Females, Headed by Female with Related Children under 18
acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel != "Other", cleanedLabel != "Total") |> 
  select(NAME,cleanedLabel,year,estimate) |> 
  mutate(`Poverty Status` = ifelse(str_detect(cleanedLabel,"Above Poverty"),"Above Poverty","Below Poverty"),
         `Family Type` = case_when(
           str_detect(cleanedLabel, "Female Householder with related children")
           ~ "Female Householder with related children",
           str_detect(cleanedLabel,"Female Householder")
           ~ "Female Householder",
           .default="All Families"
         )
  ) |> 
  select(-cleanedLabel) |>
  relocate(estimate, .after = last_col()) |> 
  relocate(year, .after = last_col()) |> 
    addPercentVar(pctVarName, totalVarValue="All Families", totalVarName = "Family Type", year=2020) |>
  addPercentVar(pctVarName, totalVarValue="All Families", totalVarName = "Family Type", year=2010) |>
  # pivot_wider(names_from = cleanedLabel,values_from = estimate) |> 
DT::datatable(
  colnames = c('Place' = 'NAME', 'Year'='year', 'Number of Families'='estimate'),
    elementId = paste0("DataTables_",tableId)

  ) |> 
  # DT::formatPercentage('Percentage of People', 0) |>
  # DT::formatCurrency('Above Poverty', currency = "", digits=0) |> 
  DT::formatCurrency('Number of Families', currency = "", digits=0) |> 
  DT::formatPercentage(pctVarName, digits=2)
tableId <- tableId+1
```

```{r}
#| label: povertyFamilyGraph
acsDf |> filter(concept=="POVERTY STATUS IN THE PAST 12 MONTHS OF FAMILIES BY FAMILY TYPE BY PRESENCE OF RELATED CHILDREN UNDER 18 YEARS BY AGE OF RELATED CHILDREN", cleanedLabel != "Other") |> 
  select(NAME,cleanedLabel,year,estimate) |> 
   mutate(`Poverty Status` = ifelse(str_detect(cleanedLabel,"Above Poverty"),"Above Poverty","Below Poverty"),
         `Family Type` = case_when(
           str_detect(cleanedLabel, "Female Householder with related children")
           ~ "Female Householder with related children",
           str_detect(cleanedLabel,"Female Householder")
           ~ "Female Householder",
           .default="All Other Families"
         )
  ) |> 
  ggplot(aes(x=`Poverty Status`,y=estimate,fill=`Family Type`))+
  geom_bar(stat="identity", position="stack")+
  labs(y="Estimated Number of Families",
       x="",
       fill="Family Type")+
  scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )
```
:::::

#### Employment by Industry
::::{.columns}
```{r}
#| label: empTable

topIndustries <- acsDf |> filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other" & cleanedLabel != "EstimateTotal" & cleanedLabel != "Total", year==currReportYear) |> 
  mutate(cleanedLabel = str_remove(cleanedLabel,"([\\w\\s\\,&]*:\\s?)")) |> 
  select(-concept) |> 
  group_by(cleanedLabel) |>
  summarize(numberOfJobs=sum(estimate)) |> 
  arrange(desc(numberOfJobs)) |> 
  top_n(numberOfTopIndustries) |> 
  select(cleanedLabel) |> 
  pull()

pctVarName <- "Percentage of Jobs"

acsDf |> 
filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other") |> 
  mutate(cleanedLabel = str_remove(cleanedLabel,"([\\w\\s\\,&]*:\\s?)"),
         cleanedLabel = ifelse(cleanedLabel %in% topIndustries | cleanedLabel == "Total", cleanedLabel, "Other Industries")) |> 
  group_by(NAME,cleanedLabel,year) |> 
  summarize(estimate=sum(estimate)) |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2020) |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2010) |> 
  filter(cleanedLabel != "EstimateTotal" & cleanedLabel != "Total") |> 
DT::datatable(
  colnames = c('Place' = 'NAME', 'Year'='year', 'Number of Jobs' = 'estimate', 'Industry'='cleanedLabel'),
    elementId = paste0("DataTables_",tableId)

  ) |> 
  DT::formatCurrency('Number of Jobs', currency='', digits=0) |> 
  DT::formatPercentage(pctVarName,digits=2)
tableId <- tableId+1
```

```{r}
#| label: empGraph
plotly::ggplotly(
acsDf |> filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other" & cleanedLabel != "EstimateTotal" & cleanedLabel != "Total",year==currReportYear) |> 
  mutate(cleanedLabel = str_remove(cleanedLabel,"([\\w\\s\\,&]*:\\s?)"),
         cleanedLabel = ifelse(cleanedLabel %in% topIndustries, cleanedLabel, "Other Industries")) |> 
  group_by(NAME,cleanedLabel,year) |> 
  summarize(estimate=sum(estimate)) |> 
  ggplot(aes(y=estimate, x=NAME, fill = cleanedLabel))+
  geom_bar(stat = "identity", position = "dodge")+
  theme(legend.position = "none")+
  labs(y="Estimated Number of Workers",
       x="Place",
       fill="Type of Tenure")+
  scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )
)

```
:::::

#### Employment by Industry (Historical)
::::{.columns}
```{r}
#| label: empHistTable

acsDf |> filter(concept == "INDUSTRY BY OCCUPATION FOR THE CIVILIAN  EMPLOYED POPULATION 16 YEARS AND OVER" & cleanedLabel != "Other" ) |> 
  mutate(cleanedLabel = str_remove(cleanedLabel,"(:[\\w\\s,&]*)")) |> 
  select(-concept) |> 
  group_by(NAME,year,cleanedLabel) |> 
  summarize(estimate=sum(estimate)) |> 
  ungroup() |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2020) |> 
  addPercentVar(pctVarName, totalVarValue="Total", year=2010) |> 
  filter(cleanedLabel != "EstimateTotal" & cleanedLabel != "Total") |> 
DT::datatable(
  colnames = c('Place' = 'NAME', 'Year'='year', 'Number of Jobs' = 'estimate', 'Industry'='cleanedLabel'),
    elementId = paste0("DataTables_",tableId)

  ) |> 
  DT::formatCurrency('Number of Jobs', currency='', digits=0) |> 
  DT::formatPercentage(pctVarName, digits=2)
tableId <- tableId+1
```
:::::
#### Labor Force by Place of Work
::::{.columns}
```{r}
#| label: placeWorkTable

acsDf |> 
  filter(concept=="MEANS OF TRANSPORTATION TO WORK BY PLACE OF WORK--STATE AND COUNTY LEVEL", cleanedLabel!="Other", cleanedLabel !="Total") |>
  select(-concept) |> 
  pivot_wider(values_from = estimate,names_from = cleanedLabel) |> 
  
DT::datatable(
    colnames = c('Place' = 'NAME', 'Year'='year'),
      elementId = paste0("DataTables_",tableId)

  ) |> 
  DT::formatCurrency('Work Out Of State', currency='', digits=0) |> 
  DT::formatCurrency('Work Out of County of Residence', currency='', digits=0) |> 
  DT::formatCurrency('Work in County of Residence', currency='', digits=0) 
tableId <- tableId+1
```

```{r}
#| label: placeWorkGraph

plotly::ggplotly(
acsDf |> filter(concept=="MEANS OF TRANSPORTATION TO WORK BY PLACE OF WORK--STATE AND COUNTY LEVEL", cleanedLabel!="Other",cleanedLabel !="Total") |> 
  ggplot(aes(x=cleanedLabel,y=estimate,fill=NAME))+
  geom_bar(stat="identity",color=barOutlineColor, position="dodge")+
  labs(y="Estimated Number of Workers",
       x="",
       fill="Place of Work")+
  scale_x_discrete(guide = guide_axis(n.dodge=3))+
   scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )
)
```
:::::
#### Commuting Patterns
::::{.columns}
```{r}
#| label: commutingTables

pctVars <- c("percentageOfJobs")
pctWholeVars <- c("")

empDataWorkSubset |> 
  bind_rows(totalWork) |> 
 DT::datatable(
  caption = "Anderson County laborers by counties where laborers reside",
  colnames = c('Home County' = 'homeCountyName', 'Number of Jobs' = 'numberOfJobs', 'Percentage of Jobs' = 'percentageOfJobs', 'Year'='year'),
    elementId = paste0("DataTables_",tableId)

  ) |> 
  DT::formatPercentage('Percentage of Jobs', 0) |> 
  DT::formatCurrency('Number of Jobs', currency = "", digits=0)
empDataHomeSubset |> 
  bind_rows(totalHome) |> 
 DT::datatable(
  caption = "Anderson County residents by counties where residents work",
  colnames = c('Work County' = 'workCountyName', 'Number of Jobs' = 'numberOfJobs', 'Percentage of Jobs' = 'percentageOfJobs','Year'='year'),
    elementId = paste0("DataTables_",tableId)

  ) |> 
  DT::formatPercentage('Percentage of Jobs', 0) |> 
  DT::formatCurrency('Number of Jobs', currency = "", digits=0)
tableId <- tableId+1
```

``` {r}
#| label: commutingGraphs
plotly::ggplotly(
(empDataWorkSubset |> 
    filter(year==currReportYear) |> 
  ggplot(aes(x=homeCountyName,y=numberOfJobs)) +
  geom_bar(stat = "identity",fill=barColor,color=barOutlineColor)+
  labs(x = "Home County", 
       y = "Number of Jobs", 
       title = "Number of Jobs by County")+
     scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )) 
  )

plotly::ggplotly(
(empDataHomeSubset |> 
    filter(year==currReportYear) |> 
  ggplot(aes(x=workCountyName,y=numberOfJobs)) +
  geom_bar(stat = "identity",fill=barColor,color=barOutlineColor)+
  labs(x = "Work County", 
       y = "Number of Jobs", 
       title = "Number of Jobs by County")+
     scale_y_continuous(
     labels = scales::comma,
     breaks=pretty_breaks()
   )) 
  )
```
:::::




# Blount
```{r}
#| label: end

```

